Zn2+ is Essential for Ca2+ Oscillations in Mouse Eggs

Version 1

Abstract

Abstract

Changes in the intracellular concentration of free calcium (Ca2+) underpin egg activation and initiation of development in animals and plants. In mammals, the Ca2+ release is periodical, known as Ca2+ oscillations, and mediated by the type 1 inositol 1,4,5-trisphosphate receptor (IP3R1). Another divalent cation, zinc (Zn2+), increases exponentially during oocyte maturation and is vital for meiotic transitions, arrests, and polyspermy prevention. It is unknown if these pivotal cations interplay during fertilization. Here, using mouse eggs, we showed that basal concentrations of labile Zn2+ are indispensable for sperm-initiated Ca2+ oscillations because Zn2+-deficient conditions induced by cell-permeable chelators abrogated Ca2+ responses evoked by fertilization and other physiological and pharmacological agonists. We also found that chemically- or genetically generated Zn2+-deficient eggs displayed reduced IP3R1 sensitivity and diminished ER Ca2+ leak despite the stable content of the stores and IP3R1 mass. Resupplying Zn2+ restarted Ca2+ oscillations, but excessive Zn2+ prevented and terminated them, hindering IP3R1 responsiveness. The findings suggest that a permissive window of Zn2+ concentrations is required for Ca2+ responses and IP3R1 function in eggs, ensuring optimal response to fertilization and egg activation.

Introduction

Vertebrate eggs are arrested at the metaphase stage of the second meiosis (MII) when ovulated because they have an active Cdk1/cyclin B complex and inactive APC/CCdc20 (Heim et al., 2018). Release from MII initiates egg activation, the first hallmark of embryonic development (Ducibella et al., 2002; Schultz and Kopf, 1995). The universal signal of egg activation is an increase in the intracellular concentration of calcium (Ca2+) (Ridgway et al., 1977; Stricker, 1999). Ca2+ release causes the inactivation of the APC/C inhibitor Emi2, which enhances cyclin B degradation and induces meiotic exit (Lorca et al., 1993; Shoji et al., 2006; Suzuki et al., 2010a). In mammals, the stereotypical fertilization Ca2+ signal, oscillations, consists of transient but periodical Ca2+ increases that promote progression into interphase (Deguchi et al., 2000; Miyazaki et al., 1986). The sperm-borne Phospholipase C zeta1 (PLCζ) persistently stimulates the production of inositol 1,4,5-trisphosphate (IP3) (Matsu-ura et al., 2019; Saunders et al., 2002; Wu et al., 2001) that binds its cognate receptor in the endoplasmic reticulum (ER), IP3R1 and causes Ca2+ release from the egg’s main Ca2+ reservoir (Wakai et al., 2019). The intake of extracellular Ca2+ via plasma membrane channels and transporters ensures the persistence of the oscillations (Miao et al., 2012; Stein et al., 2020; Wakai et al., 2019, 2013).

Before fertilization, maturing oocytes undergo cellular and biochemical modifications (see for review (Ajduk et al., 2008)). The nucleus of immature oocytes, known as the germinal vesicle (GV), undergoes the breakdown of its envelope marking the onset of maturation and setting in motion a series of cellular events that culminate with the release of the first polar body, the correct ploidy for fertilization, and re-arrest at MII (Eppig, 1996). Other organelles are also reorganized, such as cortical granules migrate to the cortex for exocytosis and polyspermy block, mitochondria undergo repositioning, and the cytoplasm’s redox state becomes progressively reduced to promote the exchange of the sperm’s protamine load (Liu, 2011; Perreault et al., 1988; Wakai et al., 2014). Wide-ranging adaptations also occur in the Ca2+ release machinery to produce timely and protracted Ca2+ oscillations following sperm entry (Fujiwara et al., 1993; Lawrence et al., 1998), including the increase in the content of the Ca2+ stores, ER reorganization with cortical cluster formation, and increased IP3R1 sensitivity (Lee et al., 2006; Wakai et al., 2012). The total intracellular levels of zinc (Zn2+) also remarkably increase during maturation, amounting to a 50% rise, which is necessary for oocytes to proceed to the telophase I of meiosis and beyond (Kim et al., 2010). Remarkably, after fertilization, Zn2+ levels need to decrease, as Emi2 is a Zn2+-associated molecule, and high Zn2 levels prevent MII exit (Bernhardt et al., 2012; Shoji et al., 2014; Suzuki et al., 2010b). Following the initiation of Ca2+ oscillations, approximately 10 to 20% of the Zn2+ accrued during maturation is ejected during the Zn2+ sparks, a conserved event in vertebrates and invertebrate species (Kim et al., 2011; Que et al., 2019; Tokuhiro and Dean, 2018; Wozniak et al., 2020; Zhang et al., 2016). The use of Zn2+ chelators such as N,N,N,N-tetrakis (2-pyridinylmethyl)-1,2-ethylenediamine (TPEN) to create Zn2+-deficient conditions buttressed the importance of Zn2+ during meiotic transitions (Kim et al., 2010; Suzuki et al., 2010b). However, whether the analogous dynamics of Ca2+ and Zn2+ during maturation imply crosstalk and Zn2+ levels modulate Ca2+ release during fertilization is unknown.

IP3Rs are the most abundant intracellular Ca2+ release channel in non-muscle cells (Berridge, 2016). They form a channel by assembling into tetramers with each subunit of ~270kDa MW (Taylor and Tovey, 2010). Mammalian eggs express the type I IP3R, the most widespread isoform (Fissore et al., 1999; Parrington et al., 1998). IP3R1 is essential for egg activation because its inhibition precludes Ca2+ oscillations (Miyazaki and Ito, 2006; Miyazaki et al., 1992; Xu et al., 2003). Myriad and occasionally cell-specific factors influence Ca2+ release through the IP3R1 (Taylor and Tovey, 2010). For example, following fertilization, IP3R1 undergoes ligand-induced degradation caused by the sperm-initiated long-lasting production of IP3 that effectively reduces the IP3R1 mass (Brind et al., 2000; Jellerette et al., 2000). Another regulatory mechanism is Ca2+, a universal cofactor, which biphasically regulates IP3Rs’ channel opening (Iino, 1990; Jean and Klee, 1986), congruent with several Ca2+ and calmodulin binding sites on the channel’s sequence (Sienaert et al., 1997; Sipma et al., 1999). Notably, Zn2+ may also participate in IP3R1 regulation. Recent studies using electron cryomicroscopy (cryoEM), a technique that allows peering into the structure of IP3R1 with a near-atomic resolution, have revealed that a helical linker (LNK) domain near the C-terminus mediates the coupling between the N- and C-terminal ends necessary for channel opening (Fan et al., 2015). The LNK domain contains a putative Zinc-finger motif proposed to be vital for IP3R1 function (Fan et al., 2015; Paknejad and Hite, 2018). Therefore, the exponential increase in Zn2+ levels in maturing oocytes, besides its essential role in meiosis progression, may optimize the IP3R1 function, revealing hitherto unknown cooperation between these cations during fertilization.

Here, we examined whether crosstalk between Ca2+ and Zn2+ is required to initiate and sustain Ca2+ oscillations and maintain Ca2+ store content in MII eggs. We found that Zn2+-deficient conditions inhibited Ca2+ release and oscillations without reducing Ca2+ stores, IP3 production, IP3R1 expression, or altering the viability of eggs or zygotes. We show instead that Zn2+ deficiency impaired IP3R1 function and lessened the receptor’s ability to gate Ca2+ release out of the ER. Remarkably, resupplying Zn2+ re-established the oscillations interrupted by low Zn2+, although persistent increases in intracellular Zn2+ were harmful, disrupting the Ca2+ responses and preventing egg activation. Together, the results show that besides contributing to oocyte maturation, Zn2+ has a central function in Ca2+ homeostasis such that optimal Zn2+ concentrations ensure IP3R1 function and the Ca2+ oscillations required for initiating embryo development.

Results

TPEN dose-dependently lowers intracellular Zn2+ and inhibits sperm-initiated Ca2+ oscillations

TPEN is a cell-permeable, non-specific chelator with a high affinity for transition metals widely used to study their function in cell physiology (Arslan et al., 1985; Lo et al., 2020). Mouse oocytes and eggs have exceedingly high intracellular concentrations of Zn2+ (Kim et al., 2011, 2010), and the TPEN-induced defects in the progression of meiosis have been ascribed to its chelation (Bernhardt et al., 2011; Kim et al., 2010). In support of this view, the Zn2+ levels of cells showed acute reduction after TPEN addition, as reported by indicators such as FluoZin-3 (Arslan et al., 1985; Suzuki et al., 2010b). Studies in mouse eggs also showed that the addition of µM concentrations of TPEN disrupted Ca2+ oscillations initiated by fertilization or SrCl2 (Lawrence et al., 1998; Suzuki et al., 2010b), but the mechanism(s) and target(s) of the inhibition remained unknown. To gain insight into this phenomenon, we first performed dose-titration studies to determine the effectiveness of TPEN in lowering Zn2+ in eggs. The addition of 2.5 µM TPEN protractedly reduced Zn2+ levels, whereas 5 and 10 µM TPEN acutely and persistently reduced FluoZin-3 fluorescence (Fig. 1A). These concentrations of TPEN are higher than the reported free Zn2+ concentrations in cells, but within range of those of found in typical culture conditions (Lo et al., 2020; Qin et al., 2011). We next determined the concentrations of TPEN required to abrogate fertilization-initiated oscillations. Following intracytoplasmic sperm injection (ICSI), we monitored Ca2+ responses while increasing TPEN concentrations. As shown in Fig. 1B, 5 and 10 µM TPEN effectively blocked ICSI-induced Ca2+ oscillations in over half of the treated cells, and the remaining eggs, after a prolonged interval, resumed lower-frequency rises (Fig. 1B-center panels). Finally, 50 µM or greater concentrations of TPEN permanently blocked these oscillations (Fig. 1B-right panel). It is noteworthy that at the time of addition, TPEN induces a sharp drop in basal Fura-2 F340/ F380 ratios, consistent with Fura-2’s high affinity for Zn2+ (Snitsarev et al., 1996).

TPEN-induced Zn2+ deficiency inhibits fertilization-initiated Ca2+ oscillations in a dose-dependent manner.

(A) (Left panel) Representative normalized Zn2+ recordings of MII eggs loaded with FluoZin-3AM following the addition of increasing concentrations of TPEN (0 µM, DMSO, black trace; 2.5 µM, sky blue; 5 µM, blue; 10 µM, navy). TPEN was directly added to the monitoring media. (Right panel) Representative fluorescent images of MII eggs loaded FluoZin-3AM supplemented with 0, 2.5, and 10 µM of TPEN. Scale bar: 10 µm. (B-D). (B) Representative Ca2+ oscillations following ICSI after the addition of 0, 5, 10, or 50 µM TPEN (arrowheads). Insets show representative traces for eggs that resumed Ca2+ oscillations after TPEN. (C) As above, but following the addition of 100 µM EDTA, 100 or 500 µM DTPA (time of addition denoted by arrowheads). (D) Ca2+ oscillations following ICSI after the addition of 50, 100, and 500 µM TPA (horizontal bars of increasing thickness). (E) Representative bright field images of ICSI fertilized eggs 2.5, 4, and 7 hr. after sperm injection. Arrows and arrowheads denote the second polar body and PN formation, respectively. Scale bar: 10 µm.

We next used membrane-permeable and -impermeable chelators to assess whether TPEN inhibited Ca2+ oscillations by chelating Zn2+ from intracellular or extracellular compartments. The addition of the high-affinity but cell-impermeable Zn2+ chelators DTPA and EDTA neither terminated nor temporarily interrupted ICSI-induced Ca2+ oscillations (Fig. 1C). Protractedly, Ca2+ oscillations slowed down, possibly because of chelation and lowering of external Ca2+ (Fig. 1C). Conversely, TPA, a permeable Zn2+ chelator, blocked the ICSI-initiated oscillations but required higher concentrations than TPEN (Fig. 1D). Collectively, the data suggest that basal levels of labile Zn2+ are essential to sustain the fertilization-initiated Ca2+ oscillations in eggs.

We next evaluated whether TPEN supplementation prevented the completion of meiosis and pronuclear (PN) formation following fertilization (Fig. 1E and Table 1). All fertilized eggs promptly extruded second polar bodies regardless of treatment (Fig. 1E). TPEN, however, impaired PN formation, and by 4- or 7-hr. post-ICSI, most treated eggs failed to show PNs, unlike controls (Fig. 1E and Table 1). Together, these results demonstrate that depletion of Zn2+ terminates Ca2+ oscillations and delays or prevents events of egg activation, including PN formation.

TPEN is a universal inhibitor of Ca2+ oscillations in eggs

Mammalian eggs initiate Ca2+ oscillations in response to numerous stimuli and conditions (Miyazaki and Ito, 2006; Wakai and Fissore, 2013). Fertilization and its release of PLCz stimulate the phosphoinositide pathway leading to the production of IP3 and Ca2+ oscillations (Miyazaki, 1988; Saunders et al., 2002). Neurotransmitters such as acetylcholine (Ach) and other G-protein coupled receptor agonists engage a similar mechanism (Dupont et al., 1996; Kang et al., 2003), although in these cases, IP3 production occurs at the plasma membrane and is short-lived (Kang et al., 2003; Swann and Parrington, 1999). Agonists such as SrCl2 and thimerosal generate oscillations by sensitizing IP3R1 without producing IP3. The mechanism(s) of SrCl2 is unclear, although its actions are reportedly directly on the IP3R1 (Hajnóczky and Thomas, 1997; Hamada et al., 2003; Nomikos et al., 2015, 2011; Sanders et al., 2018). Thimerosal oxidizes dozens of thiol groups in the receptor, which enhances the receptor’s sensitivity and ability to release Ca2+ (Bootman et al., 1992; Evellin et al., 2002; Joseph et al., 2018). We took advantage of the varied points at which the mentioned agonists engage the phosphoinositide pathway to examine TPEN’s effectiveness in inhibiting their effects. mPlcz mRNA injection, like fertilization, induces persistent Ca2+ oscillations, although mPlcz’s tends to be more robust. Consistent with this, the addition of 10 and 25 µM TPEN transiently interrupted or belatedly terminated oscillations, whereas 50 µM acutely stopped all responses (Fig. 2A). By contrast, SrCl2-initiated rises were the most sensitive to Zn2+-deficient conditions, with 2.5 µM TPEN nearly terminating all oscillations that 5 µM did (Fig. 2B). TPEN was equally effective in ending the Ach-induced Ca2+ responses (Fig. 2C), but curbing thimerosal responses required higher concentrations (Fig. 2D). Lastly, we ruled out that downregulation of IP3R1 was responsible for the slow-down or termination of the oscillations by TPEN. To accomplish this, we examined the IP3R1 mass in eggs (Jellerette et al., 2004) with and without TPEN supplementation and injection of mPlcz mRNA. By 4-h post-injection, the mRNA induced the expected down-regulation of IP3R1 reactivity vs. uninjected eggs, but in TPEN-treated and Plcz mRNA-injected eggs, the decrease was insignificant (Fig. 2F). These findings together show that Zn2+ deficiency inhibits the IP3R1-mediated Ca2+ oscillations independently of IP3 production or loss of receptor, suggesting a role of Zn2+ on IP3R1 function (Fig. 2E).

TPEN dose-dependently inhibits Ca2+ oscillations in eggs triggered by a broad-spectrum of agonists that stimulate the PI pathway or IP3R1.

(A-D) Representative Ca2+ responses induced by (A) mPlcζ mRNA microinjection (0.01 µg/µl, black traces), (B) strontium chloride (10 mM, green), (C) acetylcholine chloride (50 µM, orange), and (D) thimerosal (25 µM, purple) in MII eggs. Increasing concentrations of TPEN were added to the monitoring media (arrowheads above traces denotes the time of adding). Insets in the upper row show representative traces of eggs that stop oscillating despite others continuing to oscillate. (E) Each bar graph summarizes the TPEN effect on Ca2+ oscillations at the selected concentrations for each of the agonists in A-D. (F) Western blot showing the intensities of IP3R1 and alpha-tubulin bands in MII eggs or in eggs injected with mPlcζ mRNA and incubated or not with TPEN above (P < 0.01). Thirty eggs per lane in all cases. This experiment was repeated twice, and the mean relative intensity of each blot is shown in the bar graph below.

Zn2+ depletion reduces IP3R1-mediated Ca2+ release

To directly assess the inhibitory effects of TPEN on IP3R1 function, we used caged IP3 (cIP3) that, after short UV pulses, releases IP3 into the ooplasm (Wakai et al., 2012; Walker et al., 1987). To exclude the possible contribution of external Ca2+ to the responses, we performed the experiments in Ca2+-free media. In response to sequential cIP3 release 5 min. apart, control eggs displayed corresponding Ca2+ rises that occasionally transitioned into short-lived oscillations (Fig. 3A). The addition of TPEN after the third cIP3 release prevented the subsequent Ca2+ response and prematurely terminated the in-progress Ca2+ rises (Fig. 3B and inset). Pre-incubation of eggs with TPEN precluded cIP3-induced Ca2+ release, even after 5 sec. of UV exposure (Fig. 3C). The addition of excess ZnSO4 (100 µM) overcame TPEN’s inhibitory effects, but only if added before (Fig. 3E) and not after the addition of TPEN (Fig. 3D). Similar concentrations of MgCl2 or CaCl2 failed to reverse TPEN effects (Fig. 3F, G). Together, the results show that Zn2+ is required for IP3R1-mediated Ca2+ release downstream of IP3 production, appearing to interfere with receptor gating, as suggested by TPEN’s rapid termination of in-progress Ca2+ rises and ongoing oscillations.

TPEN inhibition of cIP3-induced Ca2+ release is precluded by ZnSO4 supplementation before TPEN exposure.

(A-G) Representative Ca2+ responses in MII eggs triggered by the release of caged IP3 (cIP3) induced by UV light pulses of increasing duration (arrows). (A) A representative control trace without TPEN, and (B) following the addition of 10 µM TPEN between the third and the fourth pulses. The broken line rectangle is magnified in the inset, farthest right side of the panel displaying the near immediate termination of an ongoing rise. (C, D) Recordings started in the presence of 10 µM TPEN but in (D) 100 µM ZnSO4 was added between the second and the third pulses. (E) Recording started in the presence of 100 µM ZnSO4 followed by the addition of 10 µM TPEN between the third and the fourth pulses. (F, G) Recording started in the presence of 100 µM MgSO4 (F) or 100 µM CaCl2 (G) and 10 µM TPEN added as above. Arrowheads above the different panels indicate the time of TPEN or divalent cation addition. (H) Bar graphs summarizing the number and percentages of eggs that responded to a given duration of UV pulses under each of the TPEN±divalent ions.

ERp44 is an ER luminal protein of the thioredoxin family that interacts with the IP3R1, reportedly inhibiting its ability to mediate Ca2+ release (Higo et al., 2005). The localization of ERp44 in the ER-Golgi intermediate compartment of somatic cells correlates with Zn2+’s availability and changes dramatically after TPEN treatment (Higo et al., 2005; Watanabe et al., 2019). To rule out the possibility that TPEN suppresses the function of IP3R1 by modifying the subcellular distribution of ERp44, we overexpressed ERp44 by injecting HA tagged-Erp44 mRNA into MII eggs and monitored the effect on Ca2+ release. TPEN did not alter the localization of ERp44 (Supplementary Fig. 1A), and overexpression of ERp44 modified neither the Ca2+ oscillations induced by agonists (Supplementary Fig. 1B) nor the effectiveness of TPEN to block them (data not shown). Thus, TPEN and Zn2+ deficiency most likely inhibits Ca2+ release by directly interfering with IP3R1 function rather than modifying this particular regulator.

Zn2+ depletion diminishes the ER Ca2+ leak and increases Ca2+ store content

Our above cIP3 results that TPEN inhibited IP3R1-mediated Ca2+ release and interrupted in-progress Ca2+ rises despite the presence of high levels of environmental IP3 suggest its actions are probably independent of IP3 binding, agreeing with an earlier report showing that TPEN did not modify IP3’s affinity for the IP3R (Richardson and Taylor, 1993). Additionally, the presence of a Zn2+-binding motif near the C-term cytoplasmic domain of the IP3R1’s channel, which is known to influence agonist-induced IP3R1 gating (Fan et al., 2015), led us to posit and examine that Zn2+ deficiency may be disturbing Ca2+ release to the cytosol and out of the ER. To probe this possibility, we queried if pre-treatment with TPEN inhibited Ca2+ release through IP3R1. We first used Thapsigargin (Tg), a Sarcoplasmic/ER Ca2+ ATPase pump inhibitor (Thastrup et al., 1990) that unmasks a constitutive Ca2+ leak out of the ER (Lemos et al., 2021); in eggs, we have demonstrated it is mediated at least in part by IP3R1 (Wakai et al., 2019). Treatment with TPEN for 15 min. slowed the Tg-induced Ca2+ leak into the cytosol, resulting in delayed and lowered amplitude Ca2+ responses (Fig. 4A; P<0.05). To test whether the reduced response to Tg means that TPEN left a temporarily increased Ca2+ content in the ER after it, we added the Ca2+ ionophore ionomycin (Io), which empties all stores independently of IP3Rs. Io-induced Ca2+ responses were 3.3-fold greater in TPEN-treated cells, supporting the view that TPEN interferes with the ER Ca2+ leak (Fig. 4A; P < 0.05). We further evaluated this concept using in vitro aged eggs that often display reduced Ca2+ store content than freshly collected counterparts (Abbott et al., 1998). After culturing eggs in the presence or absence of TPEN for 2-hr., we added Io during Ca2+ monitoring, which in TPEN-treated eggs induced bigger Ca2+ rises than in control eggs (Fig. 4B; P <0.05). We confirmed that this effect was independent of IP3R1 degradation because TPEN did not change IP3R1 reactivity in unfertilized eggs (Fig. 4C; P <0.05).

Zn2+ depletion alters Ca2+ homeostasis and increases Ca2+ store content independent of IP3R1 mass.

(A, B) Representative Ca2+ traces of MII eggs after the addition of Tg and Io in the presence or absence of TPEN. Blue trace recordings represent TPEN-treated eggs whereas gray traces represent control, untreated eggs. (A) Io was added to fresh MII eggs once Ca2+ returned to baseline after treatment with Tg. Comparisons of mean peak amplitudes after Tg and Io are shown in the bar graphs in the right panel (P < 0.001). (B) MII eggs were aged by 2-hr. incubation supplemented or not with TPEN followed by Io addition and Ca2+ monitoring (P < 0.001). (C) Western blot showing the intensities of IP3R1 bands in MII eggs freshly collected, aged by 4-hr. incubation without TPEN, and with TPEN. Thirty eggs per lane in all cases. This experiment was repeated three times. (D, E) (Left panels) Representative traces of Ca2+ values in eggs loaded with the Ca2+-sensitive dye Rhod-2 AM and the ER Ca2+reporter, D1ER (1 µg/µl mRNA). TPEN was added into the media followed 10 min. later by (D) 10 µM Tg and (E) 50 µM Ach. (Right panel) Bars represent the difference of FRET value between at the time of Tg/ Ach addition and at 3 and 5 min. later of the addition (P < 0.05). Experiments were repeated two different times for each treatment. Black and green traces represent cytosolic Ca2+ and Ca2+-ER, respectively. Blue and black arrowheads indicate the time of addition of TPEN and Tg/ Ach, respectively. (F) Basal Zn2+ level comparison in WT (open bar) and Trpv3−/−/Trpm7−/− (dKO, orange bar) MII eggs. Each plot represents the Fluozin3 measurement at 5 min. after starting monitoring. (G) (Left panel) Representative Ca2+ traces of WT (black trace) and dKO (orange trace) MII eggs after adding Tg. Insets represent the magnified traces at the peak of Ca2+ spike from different sets of eggs. (Middle panel) Individual traces of WT and dKO eggs after Tg addition. Dashed circles represent the flection point in dKO traces. (Right panel) Comparisons of mean peak amplitudes after Tg and the time between Tg addition and the Ca2+ peak are shown in the bar graphs in the right panel (P < 0.001)

Next, we used the genetically encoded FRET sensor D1ER (Palmer et al., 2004) to assess the TPEN’s effect on the ER’s relative Ca2+ levels changes following the additions of Tg or Ach. TPEN was added 10 min. before 10 µM Tg or 50 µM Ach, and we simultaneously monitored changes in cytosolic and intra-ER Ca2+ (Fig. 4D, E). For the first three min., the Tg-induced decrease in Ca2+-ER was similar between groups. However, while the drop in Ca2+ content continued in control eggs, in TPEN-treated eggs, it came to an abrupt halt, generating profound differences between the two groups (Fig. 4D; P <0.05). TPEN had even more pronounced effects following the addition of Ach, leading to a reduced- and prematurely terminated-Ca2+ release from the ER in treated eggs (Fig. 4E; P <0.05).

Lastly, we sought to use a cellular model where low labile Zn2+ occurred without pharmacology. To this end, we examined a genetic model where the two non-selective plasma membrane channels that could influx Zn2+ in maturing oocytes have been deleted (Bernhardt et al., 2017; Carvacho et al., 2016, 2013), namely, the transient receptor potential melastatin-7 (TRPM7) and TRP vanilloid 3 (TRPV3), both members of the TRP superfamily of channels (Wu et al., 2010). We found that eggs from double knockout females (dKOs) had lower labile Zn2+ levels (Fig. 4F), and the addition of Tg revealed an expanded Ca2+ store content in these eggs vs. control WT eggs (Fig. 4G). Remarkably, in dKO eggs, the Ca2+ rise induced by Tg showed a shoulder or inflection point before the peak delaying the time to peak (Fig. 4G, inset; P <0.001). These results in dKO eggs show a changed dynamic of the Tg-induced Ca2+ release, suggesting that Zn2+ deficient levels modify ER Ca2+ release independently of chelators.

Ca2+ oscillations in eggs occur within a window of Zn2+ concentrations

We next examined if resupplying Zn2+ could restart the Ca2+ oscillations terminated by Zn2+ depletion. Zn pyrithione (ZnPT) rapidly increases cellular Zn2+ upon extracellular addition (Barnett et al., 1977; Robinson, 1964). Dose titration studies and imaging fluorimetry revealed that 0.01 µM ZnPT caused subtle and protracted increases in Zn2+ levels, whereas 0.1 µM ZnPT caused rapid increases in eggs’ Zn2+ baseline (Fig. 5A). We induced detectable Ca2+ oscillations by injection of mPlcz mRNA followed by 50 µM TPEN (Fig. 5B), which terminated them. After 30 min, we added 0.1 µM ZnPT, and within 15 min. the oscillations restarted in most TPEN-treated eggs (Fig. 5C). We repeated this approach using Thimerosal (Fig. 5D, E). Adding 0.1 µM ZnPT did not restore the Ca2+ oscillations retrained by TPEN, but 0.5 µM ZnPT did so (Fig. 5E). These results demonstrate that Zn2+ plays a pivotal, enabling role in the generation of Ca2+ oscillations in mouse eggs.

Restoring Zn2+ levels with ZnPT rescues oscillations interrupted by TPEN-induced Zn2+ deficiency.

(A) Representative traces of Zn2+ in MII eggs following the addition of 0.01 to 0.1 µM concentrations of ZnTP. The broken rectangular area is amplified in the next panel to appreciate the subtle increase in basal Zn2+ caused by the addition of ZnTP. (B, C) mPlcζ mRNA (0.01 µg/µl)-induced oscillations followed by the addition of TPEN (black arrowhead) (B), or after the addition of TPEN followed by ZnPT (red arrowhead) (C). (D, E) Thimerosal (25 µM) induced oscillations using the same sequence of TPEN (D) and ZnPT (E), but higher concentrations of ZnPT were required to rescue Thimerosal-initiated oscillations (E). These experiments were repeated at least two different times.

Excessive intracellular Zn2+ inhibits Ca2+ oscillations

Zn2+ is necessary for diverse cellular functions, consistent with numerous amino acids and proteins capable of binding Zn2+ within specific and physiological ranges (Pace and Weerapana, 2014). Excessive Zn2+, however, can cause detrimental effects on cells and organisms (Broun et al., 1990; Hara et al., 2022; Sikora and Ouagazzal, 2021). Consistent with the deleterious effects of Zn2+, a previous study showed that high concentrations of ZnPT, ~50 µM, prevented SrCl2-induced egg activation and initiation of development (Bernhardt et al., 2012; Kim et al., 2011). We examined how ZnPT and excessive Zn2+ levels influence Ca2+ oscillations. Our conditions revealed that pre-incubation or continuous exposure to 0.1 µM or 1.0 µM ZnPT delayed or prevented egg activation induced by mPlcz mRNA injection (Supplementary Fig. 2). We used these ZnPT concentrations to add it into ongoing oscillations induced by ICSI and monitored the succeeding Ca2+ responses. The addition of 0.05 to 10 µM ZnPT caused an immediate elevation of the basal levels of Fura-2 and termination of the Ca2+ oscillations (Fig. 6A-D). mPlcz mRNA-initiated Ca2+ responses were also interrupted by adding 0.1 µM ZnPT, whereas untreated eggs continued oscillating (Fig. 6E, F). ZnPT also inhibited IP3R1-mediated Ca2+ release triggered by cIP3, suggesting that excessive Zn2+ directly inhibits IP3R1 function (Fig. 6G).

Excess Zn2+ hinders Ca2+ oscillations.

(A-D) ICSI-initiated Ca2+ response without (A) or following the addition of ZnPT (B, C) (the time of ZnPT addition and concentration are denoted above the tracing). (E, F) Representative Ca2+ responses induced by injection of 0.01 µg/µl mPlcζ mRNA in untreated eggs (E) or in eggs treated with 0.1 µM ZnPT followed by 10 µM TPEN first and then 50 µM (F). (G) cIP3-induced Ca2+ release as expected when the UV pulses in the absence but not in the presence of 0.05 µM ZnPT (the time of addition is denoted by a bar above the tracing). (H, I) Representative traces of Ca2+ values in eggs loaded with the Ca2+-sensitive dye Rhod-2 AM and the ER Ca2+reporter, D1ER (1 µg/µl mRNA). Uninjected and 0.01 µg/µl mPlcζ mRNA-injected eggs were monitored. After initiation and establishment of the oscillations, 0.1 µM ZnPT was added into the media followed 30 min later by 2.5 µM Io. Experiments were repeated two different times. Red and black arrowheads indicate the time of addition of ZnPT and Io, respectively.

The increased basal ratios of Fura-2 caused by the addition of ZnPT are unlikely to represent changes in basal Ca2+ levels because they would have likely caused some cellular responses such as the release of the second polar body, egg fragmentation, or cell death, neither of which happened. It might reflect, instead, Fura-2’s ability to report changes in Zn2+ levels, which was the case because the addition of TPEN lowered the Fura-2 ratios without restarting the Ca2+ oscillations (Fig. 6F). To ensure the impact of ZnPT abolishing Ca2+ oscillations was not an imaging artifact obscuring ongoing rises, we simultaneously monitored cytoplasmic and ER Ca2+ levels with Rhod-2 and D1ER, respectively. This approach allowed synchronously observing opposite Ca2+ changes in the two compartments. In uninjected eggs, the fluorescent values remained unchanged, and in mPlcz mRNA-injected eggs, the reporters’ signals displayed the expected opposite changes (Fig. 6H, I). The addition of ZnPT rapidly increased Rhod-2 signals in uninjected and oscillating eggs, unlike D1ER’s, suggesting it cannot detect changes in Zn2+ levels to this extent despite faithfully reporting Ca2+ changes. In oscillating eggs following ZnPT addition, D1ER progressively showed fewer and lower amplitude changes, consistent with the diminishing and eventual termination of the Ca2+ oscillations. Noteworthy, the basal fluorescent ratio of D1ER in these eggs remained unchanged after ZnPT, further demonstrating its unresponsiveness to Zn2+ changes of this magnitude. We confirmed that both reporters were still in working order, as the addition of Io triggered Ca2+ changes detected by both reporters (Fig. 6H, I).

Discussion

The present study demonstrates that appropriate levels of labile Zn2+ are essential for initiating and maintaining IP3R1-mediated Ca2+ oscillations in mouse eggs regardless of the initiating stimuli. Both deficient and excessive Zn2+ compromise IP3R1 sensitivity, diminishing and mostly terminating Ca2+ oscillations. The results demonstrate that IP3R1 and Zn2+ act in concert to modulate Ca2+ signals revealing previously unexplored crosstalk between these ions at fertilization (Fig. 7).

Schematic of proposed regulation of IP3R1 function by Zn2+ in eggs and fertilized zygotes.

In MII eggs, left panel, IP3R1s are in a Ca2+-release permissive state with optimal levels of cytoplasmic Ca2+ and Zn2+ and maximum ER content, but Ca2+ is maintained at resting levels by the combined actions of pumps, ER Ca2+ leak, and reduced influx. Once fertilization takes place, left center panel, robust IP3 production induced by the sperm-borne PLCζ leads to Ca2+ release through ligand-induced gating of IP3R1. Continuous IP3 production and refilling of the stores via Ca2+ influx ensure the persistence of the oscillations. Zn2+ release occurs in association with first few Ca2+ rises and cortical granule exocytosis, Zn2+ sparks, lowering Zn2+ levels but not sufficiently to inhibit IP3R1 function. Zn2+ deficiency caused by TPEN or other permeable Zn2+ chelators, right center panel, dose-dependently impairs IP3R1 function and limits Ca2+ release. We propose this is accomplished by stripping the Zn2+ bound to the residues of the zinc-finger motif in the LNK domain of IP3R1 that prevents the allosteric modulation of the gating process induced by IP3 or other agonists. We propose that excess Zn2+, right panel, also inhibits IP3R1-mediate Ca2+ release, possibly by non-specific binding of thiol groups present in cysteine residues throughout the receptor (denoted by ?). We submit that optimal Ca2+ oscillations in mouse eggs unfold in the presence of a permissive range of Zn2+concentration.

Zn2+ is an essential micronutrient for living organisms (Kaur et al., 2014) and is required for various cellular functions, such as proliferation, transcription, and metabolism (Lo et al., 2020; Maret and Li, 2009; Yamasaki et al., 2007). Studies using Zn2+ chelators have uncovered what appears to be a cell-specific, narrow window of Zn2+ concentrations needed for cellular proliferation and survival (Carraway and Dobner, 2012; Lo et al., 2020). Further, TPEN appeared especially harmful, and in a few cell lines, even low doses provoked oxidative stress, DNA fragmentation, and apoptosis (Mendivil-Perez et al., 2012). We show here that none of the Zn2+ chelators, permeable or impermeable, affected cell viability within our experimental observations, confirming findings from previous studies that employed high concentrations of TPEN to interrupt the Ca2+ oscillations (Lawrence et al., 1998) or inducing egg activation of mouse eggs (Suzuki et al., 2010b). Our data demonstrating that ~2.5 µM is the threshold concentration of TPEN in eggs that first causes noticeable changes in basal Zn2+, as revealed by FluoZin, is consistent with the ~2 to 5 µM Zn2+ concentrations in most culture media without serum supplementation (Lo et al., 2020), and with the ~100 pM basal Zn2+ in cells (Qin et al., 2011). Lastly, the effects on Ca2+ release observed here with TPEN and other chelators were due to the chelation of Zn2+, as pretreatment with ZnSO4 but not with equal or greater concentrations of MgCl2 or CaCl2 rescued the inhibition of the responses, which is consistent with results by others (Kim et al., 2010; Lawrence et al., 1998).

To identify how Zn2+ deficiency inhibits Ca2+ release in eggs, we induced Ca2+ oscillations using various stimuli and tested the effectiveness of membrane-permeable and impermeable chelators to abrogate them. Chelation of extracellular Zn2+ failed to terminate the Ca2+ responses, whereas membrane-permeable chelators did, pointing to intracellular labile Zn2+ levels as essential for Ca2+ release. All agonists used here were susceptible to inhibition by TPEN, whether their activities depended on IP3 production or allosterically induced receptor function, although the effective TPEN concentrations varied across stimuli. Some agents, such as mPlcz mRNA or thimerosal, required higher concentrations than SrCl2, Ach, or cIP3. The reason underlying the different agonists’ sensitivities to TPEN will require additional research, but the persistence of IP3 production or change in IP3R1 structure needed to induce channel gating might explain it. However, the universal abrogation of Ca2+ oscillations by TPEN supports the view drawn from cryo-EM-derived IP3R1 models that signaling molecules can allosterically induce channel gating from different starting positions in the channel by mechanically coupling the binding effect to the ion-conducting pore in the C-terminal end of IP3R (Fan et al., 2015). The cytosolic C-terminal domain of each IP3R1 subunit is alongside the IP3-binding domain of another subunit and, therefore, well positioned to sense IP3 binding and induce channel gating (Fan et al., 2015). Within each subunit, the LNK domain, which contains a Zn2+-finger motif (Fan et al., 2015), connects the opposite domains of the molecule. Although there are no reports regarding the regulation of IP3R1 sensitivity by Zn2+, such evidence exists for RyRs (Woodier et al., 2015), which also display a conserved Zn2+-finger motif (des Georges et al., 2016). Lastly, mutations of the two Cys or two His residues of this motif, without exception, resulted in inhibition or inactivation of the IP3R1 channel (Bhanumathy et al., 2012; Uchida et al., 2003). These results are consistent with the view that the C-terminal end of IP3Rs plays a dominant role in channel gating (Bhanumathy et al., 2012; Uchida et al., 2003). We propose that TPEN inhibits Ca2+ oscillations in mouse eggs because chelating Zn2+ interferes with the function of the LNK domain and its Zn2+-finger motif proposed role on the mechanical coupling induced by agonist binding to the receptor that propagates to the pore-forming region and required to gate the channel’s ion-pore (Fan et al., 2022, 2015).

In support of this possibility, TPEN-induced Zn2+ deficient conditions altered the Ca2+-releasing kinetics in resting eggs or after fertilization. Tg increases intracellular Ca2+ by inhibiting the SERCA pump (Thastrup et al., 1990) and preventing the reuptake into the ER of the ebbing Ca2+ during the basal leak. Our previous studies showed that the downregulation of IP3R1 diminishes the leak, suggesting it occurs through IP3R1 (Wakai and Fissore, 2019). Consistent with this view, TPEN pre-treatment delayed the Ca2+ response induced by Tg, implying that Zn2+ deficiency hinders Ca2+ release through IP3R1. An expected consequence would be increased Ca2+ content in the ER after Tg. Io that mobilizes Ca2+ independently of IP3Rs (Toeplitz et al., 1979) induced enhanced responses in TPEN-treated eggs vs. controls, confirming the accumulation of Ca2+-ER in Zn2+ deficient conditions. We demonstrated that this accumulation is due to hindered emptying of the Ca2+ ER evoked by agonists in Zn2+-deficient environments resulting in reduced cytosolic Ca2+ increases, as IP3R1 is the pivotal intermediary channel between these compartments. Noteworthy, the initial phase of the Tg-induced Ca2+ release out of the ER did not appear modified by TPEN, as if it was mediated by a Zn2+-insensitive Ca2+ channel(s)/transporter, contrasting with Ach-induced emptying that was abrogated from the outset. Remarkably, independently of Zn2+ chelators, emptying of Ca2+ ER was modified in a genetic model of Zn2+-deficient oocytes lacking two TRP channels, confirming the impact of Zn2+ on Ca2+ release. It is worth noting that TPEN did not reduce but increased the mass of IP3R1, which might result in the inhibition of Zn2+-dependent ubiquitin ligase Ubc7 by the Zn-deficient conditions (Webster et al., 2003). We cannot rule out that these conditions may undermine other conformational changes required to trigger IP3R1 degradation, thereby favoring the accumulation of IP3R1.

Despite accruing Zn2+ during oocyte maturation, fertilization witnesses a necessary Zn2+ release into the external milieu, known as “Zn2+ sparks” (Kim et al., 2011; Que et al., 2019, 2015). This release of Zn2+ is a conserved event in fertilization across species and is associated with several biological functions, including those related to fending off polyspermy (Kim et al., 2011; Que et al., 2019; Wozniak et al., 2020). The concomitant decrease in Zn2+ facilitates the resumption of the cell cycle and exit from the MII stage (Kim et al., 2011). Congruent with this observation, artificial manipulation that maintains high Zn2+ levels prevent egg activation (Kim et al., 2011), whereas lowering Zn2+ with chelators leads to egg activation without Ca2+ mobilization (Suzuki et al., 2010b). As posed by others, these results suggest that meiosis completion and the early stages of fertilization unfold within a narrow window of permissible Zn2+ (Kim et al., 2011, 2010). Here, we extend this concept and show that IP3R1 function and the Ca2+ oscillations in mouse eggs require this optimal level of labile Zn2+ because the Ca2+ responses interrupted by TPEN-induced Zn2+-insufficiency are rescued by restoring Zn2+ levels with ZnPT. Furthermore, unopposed increases in Zn2+ by exposure to ZnPT abrogated fertilization-initiated Ca2+ oscillations and prevented the expected egg activation events. It is unclear how excess Zn2+ disturbs the function of IP3R1. Nevertheless, IP3R1s have multiple cysteines whose oxidation enhances the receptor sensitivity to IP3 (Joseph et al., 2018), and it is possible that excessive Zn2+ aberrantly modifies them, disturbing IP3R1 structure and function. These results reveal a close association between the Zn2+ levels controlling meiotic transitions and the Ca2+ release necessary for egg activation, placing the IP3R1 at the center of the crosstalk of these two divalent cations.

Abrupt Zn2+ changes have emerged as critical signals for meiotic and mitotic transitions in oocytes, eggs, embryos, and somatic cells (Kim et al., 2011, 2010; Lo et al., 2020). Fertilization relies on prototypical Ca2+ rises and oscillations, and Zn2+ sparks are an egg activation event downstream of this Ca2+ release, establishing a functional association between these two divalent cations that continues to grow (Kim et al., 2011). Here, we show that, in addition, these cations actively crosstalk during fertilization and that the fertilization-induced Ca2+ oscillations rely on optimized IP3R1 function underpinned by ideal Zn2+ levels set during oocyte maturation. Future studies should explore if artificial alteration of Zn2+ levels can extend the fertile lifespan of eggs, improve developmental competence, or for developing non-hormonal methods of contraception.

Materials and Methods

Key resources table

N,N,N′,N′-tetrakis (2-pyridinylmethyl)-1,2-ethylenediamine (TPEN) and Zinc pyrithione (ZnPT) were dissolved in dimethyl sulfoxide (DMSO) at 10 mM and stored at −20°C until use. SrCl2, CaCl2, ZnSO4, and MgCl2 were freshly dissolved with double-sterile water at 1M and diluted with the monitoring media just before use. Ethylenediaminetetraacetic acid (EDTA) and diethylenetriaminepentaacetic acid (DTPA) were reconstituted with double-sterile water at 0.5M and 10 mM, respectively, and the pH was adjusted to 8.0. Tris(2-pyridylmethyl) amine (TPA) was diluted in DMSO at 100 mM and stored at −20°C until use. Acetylcholine chloride and Thimerosal were dissolved in double-sterile water at 550 mM and 100 mM, respectively. Acetylcholine was stored at −20°C until use, whereas Thimerosal was made fresh in each experiment.

Mice

The University of Massachusetts Institutional Animal Care and Use Committee (IACUC) approved all animal experiments and protocols. Trpm7-floxed (Trpm7fl/fl) Gdf9-Cre and Trpv3−/− mice were bred at our facility. Trpm7fl/fl mice were crossed with Trpv3−/− to generate Trpm7fl/fl; Trpv3−/− mouse line. Female Trpm7fl/fl; Trpv3−/− mice were crossed with Trpm7fl/fl; Trpv3−/−; Gdf9-cre male to generate females null for Trpv3 and with oocyte-specific deletion for Trpm7. Ear clips from offspring were collected prior to weaning, and confirmation of genotype was performed after most experiments.

Egg Collection

All gamete handling procedures are as previously reported by us (Wakai and Fissore, 2019). MII eggs were collected from the ampulla of 6- to 8-week-old female mice. Females were superovulated via intraperitoneal injections of 5 IU pregnant mare serum gonadotropin (PMSG, Sigma, St. Louis, MO) and 5 IU human chorionic gonadotropin (hCG, sigma) at 48hr. interval. Cumulus-oocyte-complexes (COCs) were obtained 13.5 hr. post-hCG injection by tearing the ampulla using forceps and needles in TL-HEPES medium. COCs were treated with 0.26% (w/v) of hyaluronidase at room temperature (RT) for 5 min to remove cumulus cells.

Intracytoplasmic sperm injection (ICSI)

ICSI was performed as previously reported by us (Kurokawa and Fissore, 2003) using described setup and micromanipulators (Narishige, Japan). Sperm from C57BL/6 or CD1 male mice (7-12 weeks old) were collected from the cauda epididymis in TL-HEPES medium, washed several times, heads separated from tails by sonication (XL2020; Heat Systems Inc., USA) for 5 s at 4°C. The sperm lysate was washed in TL-HEPES and diluted with 12% polyvinylpyrrolidone (PVP, MW = 360 kDa) to a final PVP concentration of 6%. A piezo micropipette-driving unit was used to deliver the sperm into the ooplasm (Primetech, Ibaraki, Japan); a few piezo-pulses were applied to puncture the eggs’ plasma membrane following penetration of the zona pellucida. After ICSI, eggs were either used for Ca2+ monitoring or cultured in KSOM to evaluate activation and development at 36.5°C in a humidified atmosphere containing 5% CO2.

Preparation and microinjection of mRNA

pcDNA6-mPlcζ-mEGFP, pcDNA6-CALR-D1ER-KDEL, and pcDNA6-humanERp44-HA were linearized with the restriction enzyme PmeI and in vitro transcribed using the T7 mMESSAGE mMACHINE Kit following procedures previously used in our laboratory (Ardestani et al., 2020). A poly(A) tail was added to the in vitro synthesized RNA (mRNA) using Tailing Kit followed by quantification and dilution to 0.5 μg/μL in nuclease-free water and stored at −80°C until use. Before microinjection, mPlcζ, D1ER, and ERp44 mRNA were diluted to 0.01, 1.0, and 0.5 μg/μL, respectively, in nuclease-free water, heated at 95°C for 3 min followed by centrifugation at 13400×g for 10 min at 4°C. Cytoplasm injection of mRNA was performed under microscopy equipped with micromanipulators (Narishige, Japan). The zona pellucida and the plasma membrane of MII eggs were penetrated by applying small pulses generated by the piezo micromanipulator (Primetech, Ibaraki, Japan). The preparation of the injection pipette was as for ICSI (Kurokawa and Fissore, 2003), but the diameter of the tip was ~1 μm.

Ca2+ imaging

Before Ca2+ imaging, eggs were incubated in TL-HEPES containing 1.25 μM Fura2-AM, 1.25 μM FluoZin3-AM, or 2.2 μM Rhod2-AM and 0.02% Pluronic acid for 20 min at room temperature and then washed. The fluorescent probe-loaded eggs were allowed to attach to the bottom of the glass dish (Mat-Tek Corp., Ashland, MA). Eggs were monitored simultaneously using an inverted microscope (Nikon, Melville, NY) outfitted for fluorescence measurements. Fura-2 AM, FluoZin3-AM, and Rhod2-AM fluorescencewere excited with 340 nm and 380 nm, 480 nm, and 550 nm wavelengths, respectively, every 20 sec, for different intervals according to the experimental design and as previously performed in the laboratory. The illumination was provided by a 75-W Xenon arc lamp and controlled by a filter wheel (Ludl Electronic Products Ltd., Hawthorne, NY). The emitted light above 510 nm was collected by a cooled Photometrics SenSys CCD camera (Roper Scientific, Tucson, AZ). Nikon Element software coordinated the filter wheel and data acquisition. The acquired data were saved and analyzed using Microsoft Excel and GraphPad using Prism software (Ardestani et al., 2020). For Figures 1A, 4A-C, 5A, and 6H-I, values obtained from FluoZin3-AM, Fura2-AM, or Rhod2-AM recordings were divided by the average of the first five recordings for each treatment that was used as the F0.

To estimate relative changes in Ca2+-ER, emission ratio imaging of the D1ER (YFP/CFP) was performed using a CFP excitation filter, dichroic beamsplitter, CFP and YFP emission filters (Chroma technology, Rockingham, VT; ET436/20X, 89007bs, ET480/40m, and ET535/30m). To measure Ca2+-ER and cytosolic Ca2+ simultaneously, eggs that had been injected with D1ER were loaded with Rhod-2AM, and CFP, YFP, and Rhod-2 intensities were collected every 20 seconds.

Caged IP3

Caged-IP3/PM (cIP3) was reconstituted in DMSO and stored at −20°C until use. Before injection, cIP3 stock was diluted to 0.25 mM with water and microinjected as above. After incubation in KSOM media at 37°C for 1-hr., the injected eggs were loaded with the fluorophore, 1.25 μM Fluo4-AM, and 0.02% Pluronic acid and handled as above for Fura-2 AM. The release of cIP3 was accomplished by photolysis using 0.5 to 5-sec pulses at 360 nm wavelengths. Ca2+ imaging was as above, but Fluo4 was excited at 488 nm wavelength and emitted light above 510 nm collected as above.

Western blot analysis

Cell lysates from 20-50 mouse eggs were prepared by adding 2X-Laemmli sample buffer. Proteins were separated on 5% SDS-PAGE gels and transferred to PVDF membranes (Millipore, Bedford, MA). After blocking with 5% fat-free milk + TBS, membranes were probed with the rabbit polyclonal antibody specific to IP3R1 (1:1000; a generous gift from Dr. Jan Parys, Katholieke Universiteit, Leuven, Belgium; Parys et al., 1995). Goat anti-rabbit antibody conjugated to horseradish peroxidase (HRP) was used as a secondary antibody (1:5000; Goat anti-Rabbit IgG (H+L) Cross-Adsorbed Secondary Antibody, HRP; Invitrogen, Waltham, Ma). For detection of chemiluminescence, membranes were developed using ECL Prime (Sigma) and exposed for 1–3 min to maximum sensitivity film (VWR, Radnor, PA). Broad-range pre-stained SDS–PAGE molecular weight markers (Bio-Rad, Hercules, CA) were run in parallel to estimate the molecular weight of the immunoreactive bands. The same membranes were stripped at 50°C for 30 min (62.5 mM Tris, 2% SDS, and 100 mM 2-beta mercaptoethanol) and re-probed with anti-α-tubulin monoclonal antibody (1:1000).

Immunostaining and confocal microscopy

Immunostaining was performed according to our previous study (Akizawa et al., 2021). After incubation with or without TPEN, MII eggs were fixed with 4% (w/v) paraformaldehyde in house-made phosphate-buffered saline (PBS) for 20 min at room temperature and then permeabilized for 60 min with 0.2% (v/v) Triton X-100 in PBS. Next, the eggs were blocked for 45 min with a blocking buffer containing 0.2% (w/v) skim milk, 2% (v/v) fetal bovine serum, 1% (w/v) bovine serum albumin, 0.1% (v/v) TritonX-100, 0.75% (w/v) glycine in PBS. Eggs were incubated overnight at 4°C with mouse anti-HA antibody (1:200) diluted in blocking buffer. Eggs were washed in blocking buffer 3X for 10 min, followed by incubation at room temperature for 30 min with a secondary antibody, Alexa Fluor 488 goat anti-mouse IgG (H + L) (1:400) diluted in blocking buffer. Fluorescence signals were visualized using a laser-scanning confocal microscope (Nikon A1 Resonant Confocal with six-color TIRF) fitted with a 63×, 1.4 NA oil-immersion objective lens.

Statistical analysis

Comparisons for statistical significance of experimental values between treatments and experiments were performed in three or more experiments performed on different batches of eggs in most studies. Given the number of eggs needed, WB studies were repeated twice. Prism-GraphPad software was used to perform the statistical comparisons that include unpaired Student’s t-tests, Fisher’s exact test, and One-way ANOVA followed by Tukey’s multiple comparisons, as applicable, and the production of graphs to display the data. All data are presented as mean±s.d. Differences were considered significant at P < 0.05.

eLife Assessment

This manuscript describes a compelling study demonstrating an important mechanistic role for zinc fluctuations during fertilization. The results show strong evidence that zinc availability modulates inositol triphosphate receptor and that the cytosolic zinc concentration is critical for calcium oscillations that are required for egg activation and fertilization.

Reviewer #1 (Public Review):

The study utilizes a variety of methods, chemical and expressed probes, caged release of IP3, as well as oocytes with mutations that alter zinc availability, that provide an elegant examination of how zinc deficiency and zinc excess modulate the transient and cyclic release of calcium during egg activation. In this manuscript, the authors sought to determine if there is any interplay between zinc and calcium, two divalent cations that have been demonstrated to have important roles during fertilization. They employ agents that disrupt normal zinc homeostasis and then monitor the resulting calcium oscillations during egg activation. If zinc was made unavailable via chelation with TPEN, then the calcium oscillations halted. This occurred regardless of the activation method, which included ICSI, PLC𝛇, Acetylcholine, strontium chloride, and thimerosal. This phenotype could be rescued by introducing zinc back into the egg via an ionophore, such as zinc pyrithione; however, too much zinc pyrithione also halted calcium oscillations. Taken together, these two results demonstrate that there is a threshold level of zinc that is required for proper calcium oscillations to occur.

Furthermore, the authors sought to understand how zinc affects the IP3 receptor, IP3R1. IP3R1 is the receptor that modulates the release of calcium from the endoplasmic reticulum. The authors cited a previous study that identified zinc binding sites on IP3R1. The authors highlight that there exist no studies regarding the regulation of IP3R1 by zinc; however, such studies were cited for a similar calcium channel, the RyRs. The authors use thapsigargin to inhibit the SERCA pump, leading to calcium leak from the IP3R1. TPEN blunted the amount of calcium leaked from the ER following treatment, suggesting that zinc occupancy is necessary for IP3R1 function.

The results of these experiments support the authors conclusions that zinc is essential for the IP3R1-mediated release of calcium in an oscillatory manner during egg activation. These results provide further insight into signals necessary for proper egg activation and the ultimate success of the resulting embryo.

Reviewer #2 (Public Review):

The manuscript describes more fully the relationship between zinc fluxes and calcium oscillations during egg activation by directly manipulating the level of zinc ions inside and outside the cell with chelators and ionophores and then measuring resulting changes in Ca++ oscillations. The authors have provided solid evidence consistent with their hypothesis that zinc ions regulate Ca++ oscillations by directly modulating the gating of the IP3-R which is the main calcium channel responsible for calcium release into the cytoplasm. The authors employ well established methods of calcium measurement along with various chelators, ionophores and a wide variety of methods that cause egg activation to demonstrate that an optimal level of zinc ions are required for Ca++ oscillations to occur.

Helpfully, the authors provide a model to explain their observations in Figure 7. In the model, the increase in zinc during maturation is permissive for later IP3-R gating in response to IP3 generated at fertilization. The experiments with TPEN solidly demonstrate that Zn is required because lowering free zinc, as indicated by Fluozin staining), abrogates Ca++ oscillations. This is true regardless of the method of activation. What is not clearly described in the model or in the manuscript is whether the levels of zinc at MII are simply permissive for IP3-R gating or whether there is a more acute relationship between zinc fluxes and Ca++ oscillations. In the original paper describing the zinc spark (Kim et al., ACS Chem Biol 6:716-723), the authors show that zinc efflux very closely mirrors Ca++ oscillations suggesting a more active relationship such that zinc efflux associate with each calcium spike could be necessary for terminating the Ca spike by depleting cytoplasmic Zn. There is some evidence in the present manuscript to support this. For example, in figure 3B, TPEN appears to acutely terminate a Ca spike. Whether this is repeatable is not known. Conversely, in Figure 5C and 5E, PyT leads to a rapid restoration of Ca oscillations within minutes demonstrating that changes in free Zn can cause rapid changes in Ca++ oscillations. Perhaps, rather than simply a permissive role, the normal Zn fluxes during activation may be acutely changing IP3-R gating sensitivity.

The role of TRPv3 and Trpm7 in Zn homeostasis during egg activation seems to be minor and the results in the dKO oocytes compared to TPEN are a bit confusing. In the dKO oocytes, zinc acquisition was sufficient to make it to MII suggesting Zn transport through these channels is dispensable for maturation. During activation, however, the response to Tg in dKO eggs was opposite that of TPEN, higher cytosolic Ca and increase amplitude (Figure 4G) vs lower cytoplasmic Ca and frequency for TPEN (Figure 4A). Perhaps loss of these two channels changes Ca gating independent of Zinc.

The effect of PyT on the apparent rise in cytoplasmic Ca++ in figure 6 is interpreted as caused by an artifact of high Zn concentrations. However, it is not clear that 0.05 uM PyT would necessarily increase cytoplasmic Zn to the point where FURA-2 fluorescence would increase. A simpler interpretation is that PyT allows sufficient Zn to enter the cell and keeps the IP3-R channels open causing a sustained rise in cytoplasmic Ca and preventing oscillations in Ca++. This interpretation would also preclude inhibitory effects of high Zn concentrations as shown in figure 7 which may or may not be present but are simply speculation.

Overall, this study significantly advances our understanding of egg activation and could lead to better ways of in vitro egg activation in women undergoing assisted reproduction.

Reviewer #3 (Public Review):

This study investigated the role of Zn2+ on the maintenance of Ca2+ oscillation upon fertilization. TPEN was used to reduce the level of available Zn2+ in fertilized oocytes and different inhibitors were used to pinpoint the mechanistic involvement of intracellular Zn2+ on the maintenance of Ca2+ oscillation. As also stated in the manuscript, previous studies have demonstrated the role of Zn2+ for the successful completion of meiosis/fertilization. However, the mechanistic actions of Zn2+ on the hallmark of fertilization processes such as Ca2+ oscillation has not been elucidated. A previous publication used TPEN to cease Ca2+ oscillation, but the study was not focused on the involvement of Zn2+ signal. The manuscript expands our understanding of fertilization process by describing how the level of Zn2+ regulates Ca2+ channels and stores. The manuscript is well-organized and the topic is important in early embryo development fields.

Author Response

The following is the authors’ response to the original reviews.

Reviewer #1:

We thank the reviewer for the positive evaluation of our manuscript. We have closely examined the issues raised, and below we offer a point-by-point response to each comment. In the revised manuscript below, all the introduced changes are marked with red font.

1. There may be a general typo concerning micromolar and millimolar…

Response 1: The reviewer is correct, and during the reformatting of the manuscript, in some portions of the manuscript, the units used to indicate TPEN concentrations, always µM, were switched to mM. We have corrected those mistakes.

1. In Figure 1C/Lines 150-152, the authors use DTPA and EDTA as extracellular chelators for zinc… Was the amount of zinc in the media measured and determined to be below the amount of chelator used? Additionally, these chelators are not specific for zinc, but can bind other divalent cations including calcium. Even though zinc binds more tightly than calcium to these chelators, by mass action calcium and magnesium ions may outcompete DTPA and EDTA, leaving zinc availability unperturbed. How do the authors take these interactions into account to determine that chelation of extracellular zinc has no effect on intracellular calcium oscillations? The best way to test this is to use zinc responsive fluorescent probes in a sample of the calcium- and magnesium-replete medium and see if the addition of the DTPA or EDTA alters zinc fluorescence in the cuvette.

Response 2: We tested several conditions to determine the effect of chelators on the zinc concentration of the monitoring media using commercially available Zn2+ probes. The fluorescent zinc probe FluoZin3 added extracellularly shows high fluorescence, consistent with trace amounts of zinc and possibly non-specific bindings of other cations.

Further, the media tested was replete with the concentrations of Ca2+ and Mg2+ in TLHEPES. To establish if the non-permeable external chelators we used could bind external Zn2+ despite the high concentrations of Ca2+ and Mg2+, we followed the reviewer’s suggestion of adding the chelators to the complete media in the presence of FluoZin3. The addition of EDTA caused a protracted, ~5 min, but significant decrease in FluoZin3’s fluorescence, suggesting it is effective at removing external Zn2+ despite the presence of other divalent cations (Author response image 1A). We used a second approach where we added the chelator in the presence of nominal concentrations of Ca2+ and Mg2+ to increase the chelators’ chances to find and chelate Zn2+ (Author response image 1B). Then, we injected mPlcζ mRNA, which initiated persistent but low-frequency oscillations, as expected due to the lack of external Ca2+. Remarkably, upon restoring it, the responses became of high frequency, and upon increasing Mg2+, they acquired the regular pattern, consistent with Mg2+’s inhibition of channels that mediate Ca2+ influx. These results show that the chelation of extracellular zinc does not replicate TPEN’s effect, which suggests that TPEN’s abrupt and inhibiting ability on Ca2+ oscillations is most likely due to the 43 chelation of internal Zn2+.

Cell-impermeable chelators effectively reduce Zn2+ levels in external media but do prevent initiation or continuation of Ca2+ oscillations.

(A) A representative trace of FluoZin3 fluorescence in replete monitoring media (TL-HEPES). The media was supplemented with cell-impermeable FluoZin-3, and after initiation of monitoring, the addition of EDTA (100 μM) occurred at the designated point (triangle). (B) The left black trace represents Ca2+ oscillations initiation by injection of mPlcζ mRNA (0.01 μg/μl). The oscillations were monitored in Ca2+ and Mg2+-free media and in the presence of EDTA (110 μM) to chelate residual divalent cations derived from the water source or reagents used to make the media. The right red trace represents the initiation of oscillations as above, but after a period indicated by the black and green bars, Ca2+ and Mg2+ were sequentially added back.

Noteworthy, low EDTA concentrations, 10-µM, have been used to enhance in vitro culture conditions of mammalian embryos. In fact, it is the key ingredient to overcome the two-cell block that initially prevented the in vitro development of zygotes srom inbred strains. It is unknown how EDTA mediates this effect, which is detectable in Ca2+ and Mg2+ replete media and is only effective when placed extracellularly, but it has been attributed to its ability to chelate toxic metals introduced as impurities by other media components; one study demonstrated that the Zn2+ present in the oil used to overlay the culture medium micro drops was the target (Erbach et al., Human Reproduction, 1995, 10, 3248-54). We included some of these points in the revised version of the manuscript and added this figure as Supplementary Figure 1.

1. The reviewer noted that while dKO eggs showed reduced labile zinc levels, the amount of total zinc is not determined. Further, the response to thapsigargin in dKO eggs didn’t phenocopy the profile in eggs treated with TPEN. The reviewer argued that without further experimentation, such as comparing polar body extrusion and egg activation rate between WT and dKO, it seems to be a stretch to state that these eggs are zinc deficient.

Response 3: We agree that the statement, ‘zinc deficient,’ is an overstatement without determining the total zinc levels and associated phenotypes. Therefore, in the revised version of the manuscript, we referred to dKO-derived eggs and embryos as “low-level labile Zn2+ eggs”. Our follow-up studies show that eggs from dKO females seem to undergo egg activation events, such as the timing and rate of second polar body extrusion and pronuclear formation, with a similar dynamic to WT females. Hence, we estimate that the labile Zn2+ levels in dKO eggs are not as low as those of WT eggs treated with TPEN. Consequently, these intermediate zinc levels may have subtle effects, such as changing the Thapsigargin-induced Ca2+ release through the IP3R1 without causing widespread inhibition of cellular events observed after TPEN. We would argue that this approach is significant because it can distinguish how the different cellular events and proteins and enzymes have distinct affinities or zinc requirements and, in this case, start uncovering the channel(s) present in oocytes and eggs that may contribute to regulating zinc homeostasis.

1. The reviewer pointed out that since zinc is not redox active, it is unclear how zinc could be modifying cysteine residues of IP3R1.The reviewer suggested the possibility that excess zinc is binding to the cysteines and preventing their oxidation leading to the inhibition of the IP3R1 by blocking the channel, thereby preventing calcium release.

Response 4: The reviewer correctly points out that the mechanism(s) whereby excess Zn2+ modifies the IP3R1 function is undetermined in our study. Further, our description of ‘modifying’ is ambiguous and could be misinterpreted. Data in the literature, some of which we cite in the manuscript, shows that “oxidation of cysteine residues enhances receptor’s sensitivity to ligands in various cell types”. Zn2+ preferentially binds to reduced cysteine residues, and thus, we agree with the proposed reviewer's suggestion that “excess zinc may occupy reduced cysteine residues, preventing their oxidization required to sensitize the receptor”. As noted by the reviewer, we cannot rule out that it might be directly blocking the IP3R1 channel. We have modified the corresponding paragraphs in the Discussion.

1. Line 80 and 411, there are three other reports demonstrate the zinc reallocation to the egg shell or ejection as the zinc spark; Zebrafish: Converse et al. in Sci. Reports 10, 15673 (2020); X. lavis: Seeler et al. in Nature Chem. 13, 683-691 (2021), C. elegans: Mendoza et al. in Biology of Reproduction 107(2):406-418 (2022).

Response 5: Thank you for pointing this out, and we have added these references.

1. Line 129, when discussing that Zn2+ concentrations are reduced after TPEN as visualized by FluoZin-3, the authors should cite the article in which FluoZin-3 was first reported and this result was demonstrated initially: "Detection and Imaging of Zinc Secretion from Pancreatic β-Cells Using a New Fluorescent Zinc Indicator" by Gee et al. J. Am. Chem. Soc 124, 5, 776-778.

Response 6: Thank you for pointing this out, and we have added this reference.

1. In Figure 1E/Table 1 the authors evaluated if TPEN supplementation affects meiosis and pronuclear formation; however, the timing of TPEN treatment is unclear. When was TPEN introduced? Were the eggs left in the same media containing TPEN following fertilization, or were they transferred to different media?

Response 7: Thank you for pointing this out, and we have noted the time of the addition in the figure and text.

1. Line 1011 and 1012, ZnTP should be ZnPT.

Response 8: Thank you for pointing this out, which is now corrected.

Reviewer #2:

1. The reviewer raises the question of whether a more complex relationship could exist between the levels of zinc in MII eggs by indicating, “a more active relationship such that zinc efflux associated with each calcium spike could be necessary for terminating the Ca spike by depleting cytoplasmic zinc.” The reviewer also states, “Perhaps, rather than simply a permissive role, the normal Zn fluxes during activation may be acutely changing IP3-R gating sensitivity.”

Response 1: We agree that the demonstration that TPEN dose-dependently delays and consistently terminates ongoing Ca2+ rises perhaps reflects a more nuanced relationship between cytoplasmic labile zinc concentrations, Ca2+ oscillations, and IP3R1 function. Uncovering the precise nature of this relationship would require additional studies, such as determining the impact of TPEN on IP3 binding to its cognate receptor, regulation of channel gating, and more in-depth functional-structural experiments. However, these studies will demand time and complex experimental design and are beyond the scope of the current work. Nevertheless, they are excellent suggestions for future studies.

We would argue against the reviewer’s suggestion that “zinc sparks directly contribute to shaping the oscillations.” Zn2+ released during the sparks is not labile, but Zn2+ bound to cortical granules-resident proteins, most of which are inaccessible to the cytosol and hence to IP3R1s and should not perturb its function. We examined (data not shown) that the levels of cytosolic labile Zn2+, as assessed with FluoZin3, remained steady for over three hours of Plcζ mRNA-initiated oscillations. Further, because the Zn2+ sparks cease after the third or fourth Ca2+ rise, it would mean, at the very least, that this mechanism only operates on the first few responses. Thus, while the change of cytosolic Ca2+ concentrations triggers the Zn2+ sparks, we argue that the opposite influence is unlikely to hold true.

1. The reviewer also pointed out that the role of Trpv3 and Trpm7 in Zn2+ homeostasis seems to be minor and that the effects of genetic deletion of those channels are not as clear as those obtained by TPEN. Given that dKO eggs make it to the MII and release more but not less calcium upon thapsigargin than control despite the lowered labile Zn2+ level, the reviewer speculated that the loss of those channels changes calcium gating independent of Zn2+ concentration.

Response 2: TRPV3, TRPM7, and Cav3.2 are the three channels identified to permeate Ca2+ during oocyte maturation and egg activation in mice. We and other groups have observed that in oocytes and eggs, these channels partly compensate for the absence of each other because the deletion of these channels individually has a limited effect on Ca2+ oscillations and fertility. Thus, in the case of oocytes from Trpv3 and Trpm7 dKO animals, the other plasma membrane channel(s), most likely Cav3.2, is plausibly compensating, and its enhanced function underlies the increased Ca2+ response to Thapsigargin.

Nevertheless, the slower time to the peak and the lesser steep rise of the Thapsigargin induced rise suggest a negative impact of the dKO environment on IP3R1’s ability to mediate Ca2+ release. Based on the rest of the results in the manuscript, we attribute this change to the lower levels of labile Zn2+ in dKO eggs.

1. Lastly, the reviewer noted the upregulation of the Fura-2AM following addition of ZnPT. The reviewer indicated that 0.05 uM ZnPT might not increase intracellular Zn2+ to change Fura-2 fluorescence, but it might be sufficient Zn2+ to enter the cell and keep the IP3R1 channels open causing a sustained rise in cytoplasmic calcium and preventing oscillations. Further, if this interpretation holds true, the inhibitory effects of high Zn2+ on IP3R1’s gating shown in figure 7 would be precluded.

Response 3: We acknowledge that the increased levels of Fura-2 fluorescence following the addition of ZnPT could be due to the increased Zn2+ levels acting on IP3R1, increasing its open probability, and elevating cytosolic Ca2+ levels. We have added this consideration to the discussion. Nevertheless, our evidence suggests that this is unlikely because, as shown in Figure 6 H, I, the ER-Ca2+ levels as assessed by D1ER recordings did not change following the addition of ZnPT, whereas Rhod-2 fluorescence did, suggesting that the two events are seemingly uncoupled. Further, constant leak from the ER and extended high cytosolic Ca2+ would lead to egg activation or cell death, neither of which changes were observed.

Reviewer #3:

The reviewer noted that the present study deepened the understanding of the role of zinc in regulating calcium channels and stores at fertilization beyond the previously known Zn2+ requirement in oocyte maturation and the cell cycle progression. We appreciate these comments.

1. Fig. 1. The reviewer wondered why we selected 10 μM TPEN for most of the experiments in the manuscript. The reviewer noted this concentration only stopped the Ca2+oscillations in just half of the eggs after ICSI.

Response 1: We used 10-μM TPEN throughout the study because it blocked ~50% of the oscillations of a robust trigger of Ca2+ responses such as ICSI and reduced the frequency in the remaining eggs. This concentration of TPEN abrogates and prevents the responses by milder stimuli, such as Acetylcholine and SrCl2. Importantly, thimerosal and Plcζ mRNA overcome the inhibition by 10μM but not 50-μM TPEN. However, 50μM TPEN inactivates Emi2, a Zn2+-dependent enzyme, causing parthenogenic activation and cell cycle progression, and we wanted to avoid this confounding factor. Therefore, we determined 10-μM is a “threshold” concentration and selected it for the remaining studies. We also reasoned that it would allow the detection of more subtle effects of reducing the levels of labile zinc, causing a milder inhibition of IP3R1 sensitivity and a progressive delay or modification of the responses to other agonists rather than fully abrogating them, which is the case with higher concentrations.

1. Line131 - no concentration of TPEN stated? Or 'the addition of different concentrations of TPEN"?

Response 2: We have corrected this. We have now added 50-100 µM concentrations.

1. Line 146 - instead of TPEN, all TPEN concentrations?

Response 3: We have added these corrections, as at the concentrations we tested here, 5μM TPEN and above, all caused a reduction in the baseline of Fura-2 fluorescence.

1. Line 1046 - 'We submit'? Propose?

Response 4: We have replaced the word submit for propose. Thank you for the suggestion.

Version 2

Abstract

Abstract

Changes in the intracellular concentration of free calcium (Ca2+) underpin egg activation and initiation of development in animals and plants. In mammals, the Ca2+ release is periodical, known as Ca2+ oscillations, and mediated by the type 1 inositol 1,4,5-trisphosphate receptor (IP3R1). Another divalent cation, zinc (Zn2+), increases exponentially during oocyte maturation and is vital for meiotic transitions, arrests, and polyspermy prevention. It is unknown if these pivotal cations interplay during fertilization. Here, using mouse eggs, we showed that basal concentrations of labile Zn2+ are indispensable for sperm-initiated Ca2+ oscillations because Zn2+-deficient conditions induced by cell-permeable chelators abrogated Ca2+ responses evoked by fertilization and other physiological and pharmacological agonists. We also found that chemically-or genetically generated eggs with lower levels of labile Zn2+ displayed reduced IP3R1 sensitivity and diminished ER Ca2+ leak despite the stable content of the stores and IP3R1 mass. Resupplying Zn2+ restarted Ca2+ oscillations, but excessive Zn2+ prevented and terminated them, hindering IP3R1 responsiveness. The findings suggest that a window of Zn2+ concentrations is required for Ca2+ responses and IP3R1 function in eggs, ensuring optimal response to fertilization and egg activation.

Introduction

Vertebrate eggs are arrested at the metaphase stage of the second meiosis (MII) when ovulated because they have an active Cdk1/cyclin B complex and inactive APC/CCdc20 (Heim et al., 2018). Release from MII initiates egg activation, the first hallmark of embryonic development (Ducibella et al., 2002; Schultz and Kopf, 1995). The universal signal of egg activation is an increase in the intracellular concentration of calcium (Ca2+) (Ridgway et al., 1977; Stricker, 1999). Ca2+ release causes the inactivation of the APC/C inhibitor Emi2, which enhances cyclin B degradation and induces meiotic exit (Lorca et al., 1993; Shoji et al., 2006; Suzuki et al., 2010a). In mammals, the stereotypical fertilization Ca2+ signal, oscillations, consists of transient but periodical Ca2+ increases that promote progression into interphase (Deguchi et al., 2000; Miyazaki et al., 1986). The sperm-borne Phospholipase C zeta1 (PLCζ) persistently stimulates the production of inositol 1,4,5-trisphosphate (IP3) (Matsu-ura et al., 2019; Saunders et al., 2002; Wu et al., 2001) that binds its cognate receptor in the endoplasmic reticulum (ER), IP3R1 and causes Ca2+ release from the egg’s main Ca2+ reservoir (Wakai et al., 2019). The intake of extracellular Ca2+ via plasma membrane channels and transporters ensures the persistence of the oscillations (Miao et al., 2012; Stein et al., 2020; Wakai et al., 2019, 2013).

Before fertilization, maturing oocytes undergo cellular and biochemical modifications (see for review (Ajduk et al., 2008)). The nucleus of immature oocytes, known as the germinal vesicle (GV), undergoes the breakdown of its envelope marking the onset of maturation and setting in motion a series of cellular events that culminate with the release of the first polar body, the correct ploidy for fertilization, and re-arrest at MII (Eppig, 1996). Other organelles are also reorganized, such as cortical granules migrate to the cortex for exocytosis and polyspermy block, mitochondria undergo repositioning, and the cytoplasm’s redox state becomes progressively reduced to promote the exchange of the sperm’s protamine load (Liu, 2011; Perreault et al., 1988; Wakai et al., 2014). Wide-ranging adaptations also occur in the Ca2+ release machinery to produce timely and protracted Ca2+ oscillations following sperm entry (Fujiwara et al., 1993; Lawrence et al., 1998), including the increase in the content of the Ca2+ stores, ER reorganization with cortical cluster formation, and increased IP3R1 sensitivity (Lee et al., 2006; Wakai et al., 2012). The total intracellular levels of zinc (Zn2+) also remarkably increase during maturation, amounting to a 50% rise, which is necessary for oocytes to proceed to the telophase I of meiosis and beyond (Kim et al., 2010). Remarkably, after fertilization, Zn2+ levels need to decrease, as Emi2 is a Zn2+-associated molecule, and high Zn2 levels prevent MII exit (Bernhardt et al., 2012; Shoji et al., 2014; Suzuki et al., 2010b). Following the initiation of Ca2+ oscillations, approximately 10 to 20% of the Zn2+ accrued during maturation is ejected during the Zn2+ sparks, a conserved event in vertebrates and invertebrate species (Converse and Thomas, 2020; Kim et al., 2011; Mendoza et al., 2022; Que et al., 2019; Seeler et al., 2021; Tokuhiro and Dean, 2018; Wozniak et al., 2020; Zhang et al., 2016). The use of Zn2+ chelators such as N,N,N,N-tetrakis (2-pyridinylmethyl)-1,2-ethylenediamine (TPEN) to create Zn2+-deficient conditions buttressed the importance of Zn2+ during meiotic transitions (Kim et al., 2010; Suzuki et al., 2010b). However, whether the analogous dynamics of Ca2+ and Zn2+ during maturation imply crosstalk and Zn2+ levels modulate Ca2+ release during fertilization is unknown.

IP3Rs are the most abundant intracellular Ca2+ release channel in non-muscle cells (Berridge, 2016). They form a channel by assembling into tetramers with each subunit of ∼270kDa MW (Taylor and Tovey, 2010). Mammalian eggs express the type I IP3R, the most widespread isoform (Fissore et al., 1999; Parrington et al., 1998). IP3R1 is essential for egg activation because its inhibition precludes Ca2+ oscillations (Miyazaki and Ito, 2006; Miyazaki et al., 1992; Xu et al., 2003). Myriad and occasionally cell-specific factors influence Ca2+ release through the IP3R1 (Taylor and Tovey, 2010). For example, following fertilization, IP3R1 undergoes ligand-induced degradation caused by the sperm-initiated long-lasting production of IP3 that effectively reduces the IP3R1 mass (Brind et al., 2000; Jellerette et al., 2000). Another regulatory mechanism is Ca2+, a universal cofactor, which biphasically regulates IP3Rs’ channel opening (Iino, 1990; Jean and Klee, 1986), congruent with several Ca2+ and calmodulin binding sites on the channel’s sequence (Sienaert et al., 1997; Sipma et al., 1999). Notably, Zn2+ may also participate in IP3R1 regulation. Recent studies using electron cryomicroscopy (cryoEM), a technique that allows peering into the structure of IP3R1 with a near-atomic resolution, have revealed that a helical linker (LNK) domain near the C-terminus mediates the coupling between the N-and C-terminal ends necessary for channel opening (Fan et al., 2015). The LNK domain contains a putative Zinc-finger motif proposed to be vital for IP3R1 function (Fan et al., 2015; Paknejad and Hite, 2018). Therefore, the exponential increase in Zn2+ levels in maturing oocytes, besides its essential role in meiosis progression, may optimize the IP3R1 function, revealing hitherto unknown cooperation between these cations during fertilization.

Here, we examined whether crosstalk between Ca2+ and Zn2+ is required to initiate and sustain Ca2+ oscillations and maintain Ca2+ store content in MII eggs. We found that Zn2+-deficient conditions inhibited Ca2+ release and oscillations without reducing Ca2+ stores, IP3 production, IP3R1 expression, or altering the viability of eggs or zygotes. We show instead that Zn2+ deficiency impaired IP3R1 function and lessened the receptor’s ability to gate Ca2+ release out of the ER. Remarkably, resupplying Zn2+ re-established the oscillations interrupted by low Zn2+, although persistent increases in intracellular Zn2+ were harmful, disrupting the Ca2+ responses and preventing egg activation. Together, the results show that besides contributing to oocyte maturation, Zn2+ has a central function in Ca2+ homeostasis such that optimal Zn2+ concentrations ensure IP3R1 function and the Ca2+ oscillations required for initiating embryo development.

Results

TPEN dose-dependently lowers intracellular Zn2+ and inhibits sperm-initiated Ca2+ oscillations

TPEN is a cell-permeable, non-specific chelator with a high affinity for transition metals widely used to study their function in cell physiology (Arslan et al., 1985; Lo et al., 2020). Mouse oocytes and eggs have exceedingly high intracellular concentrations of Zn2+ (Kim et al., 2011, 2010), and the TPEN-induced defects in the progression of meiosis have been ascribed to its chelation (Bernhardt et al., 2011; Kim et al., 2010). In support of this view, the Zn2+ levels of cells showed acute reduction after TPEN addition, as reported by indicators such as FluoZin-3 (Arslan et al., 1985; Gee et al., 2002; Suzuki et al., 2010b). Studies in mouse eggs also showed that the addition of low µM (40-100) concentrations of TPEN disrupted Ca2+ oscillations initiated by fertilization or SrCl2 (Lawrence et al., 1998; Suzuki et al., 2010b), but the mechanism(s) and target(s) of the inhibition remained unknown. To gain insight into this phenomenon, we first performed dose-titration studies to determine the effectiveness of TPEN in lowering Zn2+ in eggs. The addition of 2.5 µM TPEN protractedly reduced Zn2+ levels, whereas 5 and 10 µM TPEN acutely and persistently reduced FluoZin-3 fluorescence (Fig. 1A). These concentrations of TPEN are higher than the reported free Zn2+ concentrations in cells, but within range of those of found in typical culture conditions (Lo et al., 2020; Qin et al., 2011). We next determined the concentrations of TPEN required to abrogate fertilization-initiated oscillations. Following intracytoplasmic sperm injection (ICSI), we monitored Ca2+ responses while increasing TPEN concentrations. As shown in Fig. 1B, 5 and 10 µM TPEN effectively blocked ICSI-induced Ca2+ oscillations in over half of the treated cells, and the remaining eggs, after a prolonged interval, resumed lower-frequency rises (Fig. 1B-center panels). Finally, 50 µM or greater concentrations of TPEN permanently blocked these oscillations (Fig. 1B-right panel). It is noteworthy that at the time of addition, TPEN concentrations of 5 µM or above induce a sharp drop in basal Fura-2 F340/ F380 ratios, consistent with Fura-2’s high affinity for Zn2+ (Snitsarev et al., 1996). We next used membrane-permeable and -impermeable chelators to assess whether TPEN inhibited Ca2+ oscillations by chelating Zn2+ from intracellular or extracellular compartments. The addition of the high-affinity but cell-impermeable Zn2+ chelators DTPA and EDTA neither terminated nor temporarily interrupted ICSI-induced Ca2+ oscillations (Fig. 1C), although protractedly slowed them down, possibly because of chelation and lowering of external Ca2+ (Fig. 1C). These results suggest that chelation of external Zn2+ does not affect the continuation of oscillations. We cannot determine that EDTA successfully chelated all external Zn2+, but the evidence that the addition of EDTA to the monitoring media containing cell impermeable FluoZin-3 caused a marked reduction in fluorescence, suggests that a noticeable fraction of the available Zn2+ was sequestered (Supplementary Fig. 1A). Similarly, injection of mPlcζ mRNA in eggs incubated in Ca2+ and Mg2+-free media supplemented with EDTA, to maximize the chances of chelation of external Zn2+, initiated low-frequency but persistent oscillations, and addition of Ca2+ and Mg2+ restored the physiological periodicity (Supplementary Fig. 1B). Lastly, another Zn2+-permeable chelator, TPA, blocked the ICSI-initiated Ca2+ oscillations but required higher concentrations than TPEN (Fig. 1D). Collectively, the data suggest that basal levels of labile internal Zn2+ are essential to sustain the fertilization-initiated Ca2+ oscillations in eggs.

TPEN-induced Zn2+ deficiency inhibits fertilization-initiated Ca2+ oscillations in a dose-dependent manner.

(A) (Left panel) Representative normalized Zn2+ recordings of MII eggs loaded with FluoZin-3AM following the addition of increasing concentrations of TPEN (0 µM, DMSO, black trace; 2.5 µM, sky blue; 5 µM, blue; 10 µM, navy). TPEN was directly added to the monitoring media. (Right panel) Representative fluorescent images of MII eggs loaded FluoZin-3AM supplemented with 0, 2.5, and 10 µM of TPEN. Scale bar: 10 µm. (B-D). (B) Representative Ca2+ oscillations following ICSI after the addition of 0, 5, 10, or 50 µM TPEN (arrowheads). Insets show representative traces for eggs that resumed Ca2+ oscillations after TPEN. (C) As above, but following the addition of 100 µM EDTA, 100 or 500 µM DTPA (time of addition denoted by arrowheads). (D) Ca2+ oscillations following ICSI after the addition of 50, 100, and 500 µM TPA (horizontal bars of increasing thickness). (E) Representative bright field images of ICSI fertilized eggs 2.5, 4, and 7 h after sperm injection. Arrows and arrowheads denote the second polar body and PN formation, respectively. Scale bar: 10 µm.

We next evaluated whether Zn2+ depletion prevented the completion of meiosis and pronuclear (PN) formation. To this end, ICSI-fertilized eggs were cultured in the presence of 10 μM TPEN for 8h, during which the events of egg activation were examined (Fig. 1E and Table 1). All fertilized eggs promptly extruded second polar bodies regardless of treatment (Fig. 1E). TPEN, however, impaired PN formation, and by 4-or 7-h post-ICSI, most treated eggs failed to show PNs, unlike controls (Fig. 1E and Table 1). Together, these results demonstrate that depletion of Zn2+ terminates Ca2+ oscillations and delays or prevents events of egg activation, including PN formation.

TPEN is a universal inhibitor of Ca2+ oscillations in eggs

Mammalian eggs initiate Ca2+ oscillations in response to numerous stimuli and conditions (Miyazaki and Ito, 2006; Wakai and Fissore, 2013). Fertilization and its release of PLCζ stimulate the phosphoinositide pathway, producing IP3 and Ca2+ oscillations (Miyazaki, 1988; Saunders et al., 2002). Neurotransmitters such as acetylcholine (Ach) and other G-protein coupled receptor agonists engage a similar mechanism (Dupont et al., 1996; Kang et al., 2003), although in these cases, IP3 production occurs at the plasma membrane and is short-lived (Kang et al., 2003; Swann and Parrington, 1999). Agonists such as SrCl2 and thimerosal generate oscillations by sensitizing IP3R1 without producing IP3. The mechanism(s) of SrCl2 is unclear, although its actions are reportedly directly on the IP3R1 (Hajnóczky and Thomas, 1997; Hamada et al., 2003; Nomikos et al., 2015, 2011; Sanders et al., 2018). Thimerosal oxidizes dozens of thiol groups in the receptor, which enhances the receptor’s sensitivity and ability to release Ca2+ (Bootman et al., 1992; Evellin et al., 2002; Joseph et al., 2018). We took advantage of the varied points at which the mentioned agonists engage the phosphoinositide pathway to examine TPEN’s effectiveness in inhibiting their effects. mPlcζ mRNA injection, like fertilization, induces persistent Ca2+ oscillations, although mPlcζ’s tends to be more robust. Consistent with this, the addition of 10 and 25 µM TPEN transiently interrupted or belatedly terminated oscillations, whereas 50 µM acutely stopped all responses (Fig. 2A). By contrast, SrCl2-initiated rises were the most sensitive to Zn2+-deficient conditions, with 2.5 µM TPEN nearly terminating all oscillations that 5 µM did (Fig. 2B). TPEN was equally effective in ending the Ach-induced Ca2+ responses (Fig. 2C), but curbing thimerosal responses required higher concentrations (Fig. 2D). Lastly, we ruled out that downregulation of IP3R1 was responsible for the slow-down or termination of the oscillations by TPEN. To accomplish this, we examined the IP3R1 mass in eggs (Jellerette et al., 2004) with and without TPEN supplementation and injection of mPlcζ mRNA. By 4h post-injection, PLCζ induced the expected down-regulation of IP3R1 reactivity, whereas was insignificant in TPEN-treated and Plcζ mRNA-injected eggs, as it was in uninjected control eggs (Fig. 2F). These findings together show that Zn2+ deficiency inhibits the IP3R1-mediated Ca2+ oscillations independently of IP3 production or loss of receptor, suggesting a role of Zn2+ on IP3R1 function (Fig. 2E).

TPEN dose-dependently inhibits Ca2+ oscillations in eggs triggered by a broad-spectrum of agonists that stimulate the PI pathway or IP3R1.

(A-D) Representative Ca2+ responses induced by (A) mPlcζ mRNA microinjection (0.01 µg/µl, black traces), (B) strontium chloride (10 mM, green), (C) acetylcholine chloride (50 µM, orange), and (D) thimerosal (25 µM, purple) in MII eggs. Increasing concentrations of TPEN were added to the monitoring media (arrowheads above traces denotes the time of adding). Insets in the upper row show representative traces of eggs that stop oscillating despite others continuing to oscillate. (E) Each bar graph summarizes the TPEN effect on Ca2+ oscillations at the selected concentrations for each of the agonists in A-D. (F) Western blot showing the intensities of IP3R1 and alpha-tubulin bands in MII eggs or in eggs injected with mPlcζ mRNA and incubated or not with TPEN above (P < 0.01). Thirty eggs per lane in all cases. This experiment was repeated twice, and the mean relative intensity of each blot is shown in the bar graph below.

Zn2+ depletion reduces IP3R1-mediated Ca2+ release

To directly assess the inhibitory effects of TPEN on IP3R1 function, we used caged IP3 (cIP3) that, after short UV pulses, releases IP3 into the ooplasm (Wakai et al., 2012; Walker et al., 1987). To exclude the possible contribution of external Ca2+ to the responses, we performed the experiments in Ca2+-free media. In response to sequential cIP3 release 5 min apart, control eggs displayed corresponding Ca2+ rises that occasionally transitioned into short-lived oscillations (Fig. 3A). The addition of TPEN after the third cIP3 release prevented the subsequent Ca2+ response and prematurely terminated the in-progress Ca2+ rises (Fig. 3B and inset). Pre-incubation of eggs with TPEN precluded cIP3-induced Ca2+ release, even after 5 sec UV exposure (Fig. 3C). The addition of excess ZnSO4 (100 µM) overcame TPEN’s inhibitory effects only if added before (Fig. 3E) and not after the addition of TPEN (Fig. 3D). Similar concentrations of MgCl2 or CaCl2 failed to reverse TPEN effects (Fig. 3F, G). Together, the results show that Zn2+ is required for IP3R1-mediated Ca2+ release downstream of IP3 production, appearing to interfere with receptor gating, as suggested by TPEN’s rapid termination of in-progress Ca2+ rises and ongoing oscillations.

TPEN inhibition of cIP3-induced Ca2+ release is precluded by ZnSO4 supplementation before TPEN exposure.

(A-G) Representative Ca2+ responses in MII eggs triggered by the release of caged IP3 (cIP3) induced by UV light pulses of increasing duration (arrows). (A) A representative control trace without TPEN, and (B) following the addition of 10 µM TPEN between the third and the fourth pulses. The broken line rectangle is magnified in the inset, farthest right side of the panel displaying the near immediate termination of an ongoing rise. (C, D) Recordings started in the presence of 10 µM TPEN but in (D) 100 µM ZnSO4 was added between the second and the third pulses. (E) Recording started in the presence of 100 µM ZnSO4 followed by the addition of 10 µM TPEN between the third and the fourth pulses. (F, G) Recording started in the presence of 100 µM MgSO4 (F) or 100 µM CaCl2 (G) and 10 µM TPEN added as above. Arrowheads above the different panels indicate the time of TPEN or divalent cation addition. (H) Bar graphs summarizing the number and percentages of eggs that responded to a given duration of UV pulses under each of the TPEN±divalent ions.

ERp44 is an ER luminal protein of the thioredoxin family that interacts with the IP3R1, reportedly inhibiting its ability to mediate Ca2+ release (Higo et al., 2005). The localization of ERp44 in the ER-Golgi intermediate compartment of somatic cells correlates with Zn2+’s availability and changes dramatically after TPEN treatment (Higo et al., 2005; Watanabe et al., 2019). To rule out the possibility that TPEN suppresses the function of IP3R1 by modifying the subcellular distribution of ERp44, we overexpressed ERp44 by injecting HA tagged-Erp44 mRNA into MII eggs and monitored the effect on Ca2+ release. TPEN did not alter the localization of ERp44 (Supplementary Fig. 2A), and overexpression of ERp44 modified neither the Ca2+ oscillations induced by agonists (Supplementary Fig. 2B) nor the effectiveness of TPEN to block them (data not shown). Thus, TPEN and Zn2+ deficiency most likely inhibits Ca2+ release by directly interfering with IP3R1 function rather than modifying this particular regulator.

Zn2+ depletion diminishes the ER Ca2+ leak and increases Ca2+ store content

Our above cIP3 results that TPEN inhibited IP3R1-mediated Ca2+ release and interrupted in-progress Ca2+ rises despite the presence of high levels of environmental IP3 suggest its actions are probably independent of IP3 binding, agreeing with an earlier report showing that TPEN did not modify IP3’s affinity for the IP3R (Richardson and Taylor, 1993). Additionally, the presence of a Zn2+-binding motif near the C-term cytoplasmic domain of the IP3R1’s channel, which is known to influence agonist-induced IP3R1 gating (Fan et al., 2015), led us to posit and examine that Zn2+ deficiency may be disturbing Ca2+ release to the cytosol and out of the ER. To probe this possibility, we queried if pre-treatment with TPEN inhibited Ca2+ release through IP3R1. We first used Thapsigargin (Tg), a Sarcoplasmic/ER Ca2+ ATPase pump inhibitor (Thastrup et al., 1990) that unmasks a constitutive Ca2+ leak out of the ER (Lemos et al., 2021); in eggs, we have demonstrated it is mediated at least in part by IP3R1 (Wakai et al., 2019). Treatment with TPEN for 15 min slowed the Tg-induced Ca2+ leak into the cytosol, resulting in delayed and lowered amplitude Ca2+ responses (Fig. 4A; P<0.05). To test whether the reduced response to Tg means that TPEN left a temporarily increased Ca2+ content in the ER after it, we added the Ca2+ ionophore ionomycin (Io), which empties all stores independently of IP3Rs. Io-induced Ca2+ responses were 3.3-fold greater in TPEN-treated cells, supporting the view that TPEN interferes with the ER Ca2+ leak (Fig. 4A; P < 0.05). We further evaluated this concept using in vitro aged eggs that often display reduced Ca2+ store content than freshly collected counterparts (Abbott et al., 1998). After culturing eggs in the presence or absence of TPEN for 2h, we added Io during Ca2+ monitoring, which in TPEN-treated eggs induced bigger Ca2+ rises than in control eggs (Fig. 4B; P <0.05). We confirmed that this effect was independent of IP3R1 degradation because TPEN did not change IP3R1 reactivity in unfertilized eggs (Fig. 4C; P <0.05).

Zn2+ depletion alters Ca2+ homeostasis and increases Ca2+ store content independent of IP3R1 mass.

(A, B) Representative Ca2+ traces of MII eggs after the addition of Tg and Io in the presence or absence of TPEN. Blue trace recordings represent TPEN-treated eggs whereas gray traces represent control, untreated eggs. (A) Io was added to fresh MII eggs once Ca2+ returned to baseline after treatment with Tg. Comparisons of mean peak amplitudes after Tg and Io are shown in the bar graphs in the right panel (P < 0.001). (B) MII eggs were aged by 2h. incubation supplemented or not with TPEN followed by Io addition and Ca2+ monitoring (P < 0.001). (C) Western blot showing the intensities of IP3R1 bands in MII eggs freshly collected, aged by 4h. incubation without TPEN, and with TPEN. Thirty eggs per lane in all cases. This experiment was repeated three times. (D, E) (Left panels) Representative traces of Ca2+ values in eggs loaded with the Ca2+-sensitive dye Rhod-2 AM and the ER Ca2+reporter, D1ER (1 µg/µl mRNA). TPEN was added into the media followed 10 min later by (D) 10 µM Tg and (E) 50 µM Ach. (Right panel) Bars represent the difference of FRET value between at the time of Tg/ Ach addition and at 3 and 5 min later of the addition (P < 0.05). Experiments were repeated two different times for each treatment. Black and green traces represent cytosolic Ca2+ and Ca2+-ER, respectively. Blue and black arrowheads indicate the time of addition of TPEN and Tg/ Ach, respectively. (F) Basal Zn2+ level comparison in WT (open bar) and Trpv3-/-/Trpm7-/- (dKO, orange bar) MII eggs. Each plot represents the Fluozin3 measurement at 5 min after starting monitoring. (G) (Left panel) Representative Ca2+ traces of WT (black trace) and dKO (orange trace) MII eggs after adding Tg. Insets represent the magnified traces at the peak of Ca2+ spike from different sets of eggs. (Middle panel) Individual traces of WT and dKO eggs after Tg addition. Dashed circles represent the flection point in dKO traces. (Right panel) Comparisons of mean peak amplitudes after Tg and the time between Tg addition and the Ca2+ peak are shown in the bar graphs in the right panel (P < 0.001).

Next, we used the genetically encoded FRET sensor D1ER (Palmer et al., 2004) to assess the TPEN’s effect on the ER’s relative Ca2+ levels changes following the additions of Tg or Ach. TPEN was added 10 min before 10 µM Tg or 50 µM Ach, and we simultaneously monitored changes in cytosolic and intra-ER Ca2+ (Fig. 4D, E). For the first three min, the Tg-induced decrease in Ca2+-ER was similar between groups. However, while the drop in Ca2+ content continued in control eggs, in TPEN-treated eggs, it came to an abrupt halt, generating profound differences between the two groups (Fig. 4D; P <0.05). TPEN had even more pronounced effects following the addition of Ach, leading to a reduced-and prematurely terminated-Ca2+ release from the ER in treated eggs (Fig. 4E; P <0.05).

Lastly, we sought to use a cellular model where low labile Zn2+ occurred without pharmacology. To this end, we examined a genetic model where the two non-selective plasma membrane channels that could influx Zn2+ in maturing oocytes have been deleted (Bernhardt et al., 2017; Carvacho et al., 2016, 2013), namely, the transient receptor potential melastatin-7 (TRPM7) and TRP vanilloid 3 (TRPV3), both members of the TRP superfamily of channels (Wu et al., 2010). We found that eggs from double knockout females (dKOs) had lower levels of labile Zn2+ (Fig. 4F), and the addition of Tg revealed an expanded Ca2+ store content in these eggs vs. control WT eggs (Fig. 4G). Remarkably, in dKO eggs, the Ca2+ rise induced by Tg showed a shoulder or inflection point before the peak delaying the time to peak (Fig. 4G, inset; P <0.001). These results in dKO eggs show a changed dynamic of the Tg-induced Ca2+ release, suggesting that lower levels of labile Zn2+ modify ER Ca2+ release independently of chelators.

Ca2+ oscillations in eggs occur within a window of Zn2+ concentrations

We next examined if resupplying Zn2+ could restart the Ca2+ oscillations terminated by Zn2+ depletion. Zn pyrithione (ZnPT) rapidly increases cellular Zn2+ upon extracellular addition (Barnett et al., 1977; Robinson, 1964). Dose titration studies and imaging fluorimetry revealed that 0.01 µM ZnPT caused subtle and protracted increases in Zn2+ levels, whereas 0.1 µM ZnPT caused rapid increases in eggs’ Zn2+ baseline (Fig. 5A). We induced detectable Ca2+ oscillations by injection of mPlcζ mRNA followed by 50 µM TPEN (Fig. 5B), which terminated them. After 30 min, we added 0.1 µM ZnPT, and within 15 min the oscillations restarted in most TPEN-treated eggs (Fig. 5C). We repeated this approach using Thimerosal (Fig. 5D, E). Adding 0.1 µM ZnPT did not restore the Ca2+ oscillations retrained by TPEN, but 0.5 µM ZnPT did so (Fig. 5E). These results demonstrate that Zn2+ plays a pivotal, enabling role in the generation of Ca2+ oscillations in mouse eggs.

Restoring Zn2+ levels with ZnPT rescues oscillations interrupted by TPEN-induced Zn2+ deficiency.

(A) Representative traces of Zn2+ in MII eggs following the addition of 0.01 to 0.1 µM concentrations of ZnPT. The broken rectangular area is amplified in the next panel to appreciate the subtle increase in basal Zn2+ caused by the addition of ZnPT. (B, C) mPlcζ mRNA (0.01 µg/µl)-induced oscillations followed by the addition of TPEN (black arrowhead) (B), or after the addition of TPEN followed by ZnPT (red arrowhead) (C). (D, E) Thimerosal (25 µM) induced oscillations using the same sequence of TPEN (D) and ZnPT (E), but higher concentrations of ZnPT were required to rescue Thimerosal-initiated oscillations (E). These experiments were repeated at least two different times.

Excessive intracellular Zn2+ inhibits Ca2+ oscillations

Zn2+ is necessary for diverse cellular functions, consistent with numerous amino acids and proteins capable of binding Zn2+ within specific and physiological ranges (Pace and Weerapana, 2014). Excessive Zn2+, however, can cause detrimental effects on cells and organisms (Broun et al., 1990; Hara et al., 2022; Sikora and Ouagazzal, 2021). Consistent with the deleterious effects of Zn2+, a previous study showed that high concentrations of ZnPT, ∼50 µM, prevented SrCl2-induced egg activation and initiation of development (Bernhardt et al., 2012; Kim et al., 2011). We examined how ZnPT and excessive Zn2+ levels influence Ca2+ oscillations. Our conditions revealed that pre-incubation or continuous exposure to 0.1 µM or 1.0 µM ZnPT delayed or prevented egg activation induced by mPlcζ mRNA injection (Supplementary Fig. 3). We used these ZnPT concentrations to add it into ongoing oscillations induced by ICSI and monitored the succeeding Ca2+ responses. The addition of 0.05 to 10 µM ZnPT caused an immediate elevation of the basal levels of Fura-2 and termination of the Ca2+ oscillations (Fig. 6A-D). mPlcζ mRNA-initiated Ca2+ responses were also interrupted by adding 0.1 µM ZnPT, whereas untreated eggs continued oscillating (Fig. 6E, F). ZnPT also inhibited IP3R1-mediated Ca2+ release triggered by cIP3, suggesting that excessive Zn2+ directly inhibits IP3R1 function (Fig. 6G).

Excess Zn2+ hinders Ca2+ oscillations.

(A-D) ICSI-initiated Ca2+ response without (A) or following the addition of ZnPT (B, C) (the time of ZnPT addition and concentration are denoted above the tracing). (E, F) Representative Ca2+ responses induced by injection of 0.01 µg/µl mPlcζ mRNA in untreated eggs (E) or in eggs treated with 0.1 µM ZnPT followed by 10 µM TPEN first and then 50 µM (F). (G) cIP3-induced Ca2+ release as expected when the UV pulses in the absence but not in the presence of 0.05 µM ZnPT (the time of addition is denoted by a bar above the tracing). (H, I) Representative traces of Ca2+ values in eggs loaded with the Ca2+-sensitive dye Rhod-2 AM and the ER Ca2+reporter, D1ER (1 µg/µl mRNA). Uninjected and 0.01 µg/µl mPlcζ mRNA-injected eggs were monitored. After initiation and establishment of the oscillations, 0.1 µM ZnPT was added into the media followed 30 min later by 2.5 µM Io. Experiments were repeated two different times. Red and black arrowheads indicate the time of addition of ZnPT and Io, respectively.

A noticeable feature of ZnPT is the increased basal ratios of Fura-2 AM. These changes could reflect enhanced IP3R1 function and increased basal Ca2+ concentrations caused by Zn2+ stimulation of IP3R1. This seems unlikely, however, because extended elevated cytosolic Ca2+ would probably induce cellular responses, such as the release of the second polar body, egg fragmentation, or cell death, neither of which happened. It might reflect, instead, Fura-2’s ability to report changes in Zn2+ levels, which seemed the case because the addition of TPEN lowered fluorescence without restarting the Ca2+ oscillations (Fig. 6F). To ensure the impact of ZnPT abolishing Ca2+ oscillations was not an imaging artifact obscuring ongoing rises, we simultaneously monitored cytoplasmic and ER Ca2+ levels with Rhod-2 and D1ER, respectively. This approach allowed synchronously observing Ca2+ changes in both compartments that should unfold in opposite directions. In control, uninjected eggs, the fluorescent values for both reporters remained unchanged during the monitoring period, whereas in mPlcζ mRNA-injected eggs, the reporters’ signals displayed simultaneous but opposite changes, as expected (Fig. 6H, I). The addition of ZnPT in uninjected eggs rapidly increased Rhod-2 signals but not D1ER’s, which was also the case in oscillating eggs, as the addition of ZnPT did not immediately alter the dynamics of the ER’s Ca2+ release, suggesting D1ER faithfully reports in Ca2+ changes but cannot detect changes in Zn2+ levels, at least to this extent; ZnPT progressively caused fewer and lower amplitude changes in D1ER fluorescence, consistent with the diminishing and eventual termination of the Ca2+ oscillations. Noteworthy, in these eggs, the basal D1ER fluorescent ratio remained unchanged after ZnPT, demonstrating its unresponsiveness to Zn2+ changes of this magnitude. The ZnPT-induced increases in Rhod-2 fluorescence without concomitant changes in D1ER values suggest that the changes in the dyes’ fluorescence do not represent an increase in basal Ca2+ and, more likely, signal an increase in intracellular Zn2+. We confirmed that both reporters were still in working order, as the addition of Io triggered Ca2+ changes detected by both reporters (Fig. 6H, I).

Discussion

The present study demonstrates that appropriate levels of labile Zn2+ are essential for initiating and maintaining IP3R1-mediated Ca2+ oscillations in mouse eggs regardless of the initiating stimuli. Both deficient and excessive Zn2+ compromise IP3R1 sensitivity, diminishing and mostly terminating Ca2+ oscillations. The results demonstrate that IP3R1 and Zn2+ act in concert to modulate Ca2+ signals, revealing previously unexplored crosstalk between these ions at fertilization (Fig. 7).

Schematic of proposed regulation of IP3R1 function by Zn2+ in eggs and fertilized zygotes.

In MII eggs, left panel, IP3R1s are in a Ca2+-release permissive state with optimal levels of cytoplasmic Ca2+ and Zn2+ and maximum ER content, but Ca2+ is maintained at resting levels by the combined actions of pumps, ER Ca2+ leak, and reduced influx. Once fertilization takes place, left center panel, robust IP3 production induced by the sperm-borne PLCζ leads to Ca2+ release through ligand-induced gating of IP3R1. Continuous IP3 production and refilling of the stores via Ca2+ influx ensure the persistence of the oscillations. Zn2+ release occurs in association with first few Ca2+ rises and cortical granule exocytosis, Zn2+ sparks, lowering Zn2+ levels but not sufficiently to inhibit IP3R1 function. Zn2+ deficiency caused by TPEN or other permeable Zn2+ chelators, right center panel, dose-dependently impairs IP3R1 function and limits Ca2+ release. We propose this is accomplished by stripping the Zn2+ bound to the residues of the zinc-finger motif in the LNK domain of IP3R1 that prevents the allosteric modulation of the gating process induced by IP3 or other agonists. We propose that excess Zn2+, right panel, also inhibits IP3R1-mediate Ca2+ release, possibly by non-specific binding of thiol groups present in cysteine residues throughout the receptor (denoted by a ?). We submit that optimal Ca2+ oscillations in mouse eggs unfold in the presence of a permissive range of Zn2+ concentration.

Zn2+ is an essential micronutrient for living organisms (Kaur et al., 2014) and is required for various cellular functions, such as proliferation, transcription, and metabolism (Lo et al., 2020; Maret and Li, 2009; Yamasaki et al., 2007). Studies using Zn2+ chelators have uncovered what appears to be a cell-specific, narrow window of Zn2+ concentrations needed for cellular proliferation and survival (Carraway and Dobner, 2012; Lo et al., 2020). Further, TPEN appeared especially harmful, and in a few cell lines, even low doses provoked oxidative stress, DNA fragmentation, and apoptosis (Mendivil-Perez et al., 2012). We show here that none of the Zn2+ chelators, permeable or impermeable, affected cell viability within our experimental observations, confirming findings from previous studies that employed high concentrations of TPEN to interrupt the Ca2+ oscillations (Lawrence et al., 1998) or inducing egg activation of mouse eggs (Suzuki et al., 2010b). Our data demonstrating that ∼2.5 µM is the threshold concentration of TPEN in eggs that first causes noticeable changes in basal Zn2+, as revealed by FluoZin, is consistent with the ∼2 to 5-µM Zn2+ concentrations in most culture media without serum supplementation (Lo et al., 2020), and with the ∼100 pM basal Zn2+ in cells (Qin et al., 2011). Lastly, the effects on Ca2+ release observed here with TPEN and other chelators were due to the chelation of Zn2+, as pretreatment with ZnSO4 but not with equal or greater concentrations of MgCl2 or CaCl2 rescued the inhibition of the responses, which is consistent with results by others (Kim et al., 2010; Lawrence et al., 1998).

To identify how Zn2+ deficiency inhibits Ca2+ release in eggs, we induced Ca2+ oscillations using various stimuli and tested the effectiveness of membrane-permeable and impermeable chelators to abrogate them. Chelation of extracellular Zn2+ failed to terminate the Ca2+ responses, whereas membrane-permeable chelators did, pointing to intracellular labile Zn2+ levels as essential for Ca2+ release. All agonists used here were susceptible to inhibition by TPEN, whether their activities depended on IP3 production or allosterically induced receptor function, although the effective TPEN concentrations varied across stimuli. Some agents, such as mPlcζ mRNA or thimerosal, required higher concentrations than SrCl2, Ach, or cIP3. The reason underlying the different agonists’ sensitivities to TPEN will require additional research, but the persistence of IP3 production or change in IP3R1 structure needed to induce channel gating might explain it. However, the universal abrogation of Ca2+ oscillations by TPEN supports the view drawn from cryo-EM-derived IP3R1 models that signaling molecules can allosterically induce channel gating from different starting positions in the receptor by mechanically coupling the binding effect to the ion-conducting pore in the C-terminal end of IP3R (Fan et al., 2015). The cytosolic C-terminal domain of each IP3R1 subunit is alongside the IP3-binding domain of another subunit and, therefore, well positioned to sense IP3 binding and induce channel gating (Fan et al., 2015). Within each subunit, the LNK domain, which contains a Zn2+-finger motif (Fan et al., 2015), connects the opposite domains of the molecule. Although there are no reports regarding the regulation of IP3R1 sensitivity by Zn2+, such evidence exists for RyRs (Woodier et al., 2015), which also display a conserved Zn2+-finger motif (des Georges et al., 2016). Lastly, mutations of the two Cys or two His residues of this motif, without exception, resulted in inhibition or inactivation of the IP3R1 channel (Bhanumathy et al., 2012; Uchida et al., 2003). These results are consistent with the view that the C-terminal end of IP3Rs plays a dominant role in channel gating (Bhanumathy et al., 2012; Uchida et al., 2003). We propose that TPEN inhibits Ca2+ oscillations in mouse eggs because chelating Zn2+ interferes with the function of the LNK domain and its Zn2+-finger motif proposed role on the mechanical coupling induced by agonist binding to the receptor that propagates to the pore-forming region and required to gate the channel’s ion-pore (Fan et al., 2022, 2015).

In support of this possibility, TPEN-induced Zn2+ deficient conditions altered the Ca2+-releasing kinetics in resting eggs or after fertilization. Tg increases intracellular Ca2+ by inhibiting the SERCA pump (Thastrup et al., 1990) and preventing the reuptake into the ER of the ebbing Ca2+ during the basal leak. Our previous studies showed that the downregulation of IP3R1 diminishes the leak, suggesting it occurs through IP3R1 (Wakai and Fissore, 2019). Consistent with this view, TPEN pre-treatment delayed the Ca2+ response induced by Tg, implying that Zn2+ deficiency hinders Ca2+ release through IP3R1. An expected consequence would be increased Ca2+ content in the ER after Tg. Io that mobilizes Ca2+ independently of IP3Rs (Toeplitz et al., 1979) induced enhanced responses in TPEN-treated eggs vs. controls, confirming the accumulation of Ca2+-ER in Zn2+ deficient conditions. We demonstrated that this accumulation is due to hindered emptying of the Ca2+ ER evoked by agonists in Zn2+-deficient environments, resulting in reduced cytosolic Ca2+ increases, as IP3R1 is the pivotal intermediary channel between these compartments. Noteworthy, the initial phase of the Tg-induced Ca2+ release out of the ER did not appear modified by TPEN, as if it was mediated by a Zn2+-insensitive Ca2+ channel(s)/transporter, contrasting with the abrogation of Ach-induced ER emptying from the outset. Remarkably, independently of Zn2+ chelators, emptying of Ca2+ ER was modified in a genetic model of Zn2+-deficient oocytes lacking two TRP channels, confirming the impact of Zn2+ on Ca2+ release. It is worth noting that TPEN did not reduce but maintained or increased the mass of IP3R1, which might result in the inhibition of Zn2+-dependent ubiquitin ligase Ubc7 by the Zn-deficient conditions (Webster et al., 2003). We cannot rule out that these conditions may undermine other conformational changes required to trigger IP3R1 degradation, thereby favoring the accumulation of IP3R1.

Despite accruing Zn2+ during oocyte maturation, fertilization witnesses a necessary Zn2+ release into the external milieu, known as “Zn2+ sparks” (Kim et al., 2011; Que et al., 2019, 2015). This release of Zn2+ is a conserved event in fertilization across species and is associated with several biological functions, including those related to fending off polyspermy (Kim et al., 2011; Que et al., 2019; Wozniak et al., 2020). The concomitant decrease in Zn2+ facilitates the resumption of the cell cycle and exit from the MII stage (Kim et al., 2011). Congruent with this observation, artificial manipulation that maintains high Zn2+ levels prevents egg activation (Kim et al., 2011), whereas lowering Zn2+ with chelators leads to egg activation without Ca2+ mobilization (Suzuki et al., 2010b). As posed by others, these results suggest that meiosis completion and the early stages of fertilization unfold within a narrow window of permissible Zn2+ (Kim et al., 2011, 2010). Here, we extend this concept and show that IP3R1 function and the Ca2+ oscillations in mouse eggs require this optimal level of labile Zn2+ because the Ca2+ responses interrupted by TPEN-induced Zn2+-insufficiency are rescued by restoring Zn2+ levels with ZnPT. Furthermore, unopposed increases in Zn2+ by exposure to ZnPT abrogated fertilization-initiated Ca2+ oscillations and prevented the expected egg activation events. It is unclear how excess Zn2+ disturbs the function of IP3R1. Nevertheless, IP3R1s have multiple cysteines whose oxidation enhances the receptor sensitivity to IP3 (Joseph et al., 2018), and it is possible that excessive Zn2+ aberrantly modifies them, disturbing IP3R1 structure and function or, alternatively, preventing their oxidation and sensitization of the receptor. Lastly, we cannot rule out that high Zn2+ levels directly inhibit the receptor’s channel. These results reveal a close association between the Zn2+ levels controlling meiotic transitions and the Ca2+ release necessary for egg activation, placing the IP3R1 at the center of the crosstalk of these two divalent cations.

Abrupt Zn2+ changes have emerged as critical signals for meiotic and mitotic transitions in oocytes, eggs, embryos, and somatic cells (Kim et al., 2011, 2010; Lo et al., 2020). Fertilization relies on prototypical Ca2+ rises and oscillations, and Zn2+ sparks are an egg activation event downstream of this Ca2+ release, establishing a functional association between these two divalent cations that continues to grow (Kim et al., 2011). Here, we show that, in addition, these cations actively crosstalk during fertilization and that the fertilization-induced Ca2+ oscillations rely on optimized IP3R1 function underpinned by ideal Zn2+ levels set during oocyte maturation. Future studies should explore if artificial alteration of Zn2+ levels can extend the fertile lifespan of eggs, improve developmental competence, or develop methods of non-hormonal contraception.

Materials and Methods

Key resources table

N,N,N′,N′-tetrakis (2-pyridinylmethyl)-1,2-ethylenediamine (TPEN) and Zinc pyrithione (ZnPT) were dissolved in dimethyl sulfoxide (DMSO) at 10 mM and stored at -20°C until use. SrCl2, CaCl2, ZnSO4, and MgCl2 were freshly dissolved with double-sterile water at 1M and diluted with the monitoring media just before use. Ethylenediaminetetraacetic acid (EDTA) and diethylenetriaminepentaacetic acid (DTPA) were reconstituted with double-sterile water at 0.5M and 10 mM, respectively, and the pH was adjusted to 8.0. Tris(2-pyridylmethyl) amine (TPA) was diluted in DMSO at 100 mM and stored at -20°C until use. Acetylcholine chloride and Thimerosal were dissolved in double-sterile water at 550 mM and 100 mM, respectively. Acetylcholine was stored at -20°C until use, whereas Thimerosal was made fresh in each experiment.

Mice

The University of Massachusetts Institutional Animal Care and Use Committee (IACUC) approved all animal experiments and protocols. Trpm7-floxed (Trpm7fl/fl) Gdf9-Cre and Trpv3−/− mice were bred at our facility. Trpm7fl/fl mice were crossed with Trpv3−/− to generate Trpm7fl/fl; Trpv3−/− mouse line. Female Trpm7fl/fl; Trpv3−/− mice were crossed with Trpm7fl/fl; Trpv3−/−; Gdf9-cre male to generate females null for Trpv3 and with oocyte-specific deletion for Trpm7. Ear clips from offspring were collected prior to weaning, and confirmation of genotype was performed after most experiments.

Egg Collection

All gamete handling procedures are as previously reported by us (Wakai and Fissore, 2019). MII eggs were collected from the ampulla of 6- to 8-week-old female mice. Females were superovulated via intraperitoneal injections of 5 IU pregnant mare serum gonadotropin (PMSG, Sigma, St. Louis, MO) and 5 IU human chorionic gonadotropin (hCG, sigma) at 48hr. interval. Cumulus-oocyte-complexes (COCs) were obtained 13.5 hr. post-hCG injection by tearing the ampulla using forceps and needles in TL-HEPES medium. COCs were treated with 0.26% (w/v) of hyaluronidase at room temperature (RT) for 5 min to remove cumulus cells.

Intracytoplasmic sperm injection (ICSI)

ICSI was performed as previously reported by us (Kurokawa and Fissore, 2003) using described setup and micromanipulators (Narishige, Japan). Sperm from C57BL/6 or CD1 male mice (7-12 weeks old) were collected from the cauda epididymis in TL-HEPES medium, washed several times, heads separated from tails by sonication (XL2020; Heat Systems Inc., USA) for 5 s at 4°C. The sperm lysate was washed in TL-HEPES and diluted with 12% polyvinylpyrrolidone (PVP, MW = 360 kDa) to a final PVP concentration of 6%. A piezo micropipette-driving unit was used to deliver the sperm into the ooplasm (Primetech, Ibaraki, Japan); a few piezo-pulses were applied to puncture the eggs’ plasma membrane following penetration of the zona pellucida. After ICSI, eggs were either used for Ca2+ monitoring or cultured in KSOM to evaluate activation and development at 36.5°C in a humidified atmosphere containing 5% CO2.

Preparation and microinjection of mRNA

pcDNA6-mPlcζ-mEGFP, pcDNA6-CALR-D1ER-KDEL, and pcDNA6-humanERp44-HA were linearized with the restriction enzyme PmeI and in vitro transcribed using the T7 mMESSAGE mMACHINE Kit following procedures previously used in our laboratory (Ardestani et al., 2020). A poly(A) tail was added to the in vitro synthesized RNA (mRNA) using Tailing Kit followed by quantification and dilution to 0.5 μg/μL in nuclease-free water and stored at -80°C until use. Before microinjection, mPlcζ, D1ER, and ERp44 mRNA were diluted to 0.01, 1.0, and 0.5 μg/μL, respectively, in nuclease-free water, heated at 95°C for 3 min followed by centrifugation at 13400×g for 10 min at 4°C. Cytoplasm injection of mRNA was performed under microscopy equipped with micromanipulators (Narishige, Japan). The zona pellucida and the plasma membrane of MII eggs were penetrated by applying small pulses generated by the piezo micromanipulator (Primetech, Ibaraki, Japan). The preparation of the injection pipette was as for ICSI (Kurokawa and Fissore, 2003), but the diameter of the tip was ∼1 μm.

Ca2+ and Zn2+ imaging

Before Ca2+ imaging, eggs were incubated in TL-HEPES containing 1.25 μM Fura2-AM, 1.25 μM FluoZin3-AM, or 2.2 μM Rhod2-AM and 0.02% Pluronic acid for 20 min at room temperature and then washed. The fluorescent probe-loaded eggs were allowed to attach to the bottom of the glass dish (Mat-Tek Corp., Ashland, MA). Eggs were monitored simultaneously using an inverted microscope (Nikon, Melville, NY) outfitted for fluorescence measurements. Fura-2 AM, FluoZin3-AM, and Rhod2-AM fluorescence were excited with 340 nm and 380 nm, 480 nm, and 550 nm wavelengths, respectively, every 20 sec, for different intervals according to the experimental design and as previously performed in the laboratory. The illumination was provided by a 75-W Xenon arc lamp and controlled by a filter wheel (Ludl Electronic Products Ltd., Hawthorne, NY). The emitted light above 510 nm was collected by a cooled Photometrics SenSys CCD camera (Roper Scientific, Tucson, AZ). Nikon Element software coordinated the filter wheel and data acquisition. The acquired data were saved and analyzed using Microsoft Excel and GraphPad using Prism software (Ardestani et al., 2020). For Figures 1A, 4A-C, 5A, and 6H-I, values obtained from FluoZin3-AM, Fura2-AM, or Rhod2-AM recordings were divided by the average of the first five recordings for each treatment that was used as the F0.

To estimate relative changes in Ca2+-ER, emission ratio imaging of the D1ER (YFP/CFP) was performed using a CFP excitation filter, dichroic beamsplitter, CFP and YFP emission filters (Chroma technology, Rockingham, VT; ET436/20X, 89007bs, ET480/40m, and ET535/30m). To measure Ca2+-ER and cytosolic Ca2+ simultaneously, eggs that had been injected with D1ER were loaded with Rhod-2AM, and CFP, YFP, and Rhod-2 intensities were collected every 20 sec.

Caged IP3

Caged-IP3/PM (cIP3) was reconstituted in DMSO and stored at -20°C until use. Before injection, cIP3 stock was diluted to 0.25 mM with water and microinjected as above. After incubation in KSOM media at 37°C for 1-hr., the injected eggs were loaded with the fluorophore, 1.25 μM Fluo4-AM, and 0.02% Pluronic acid and handled as above for Fura-2 AM. The release of cIP3 was accomplished by photolysis using 0.5 to 5-sec pulses at 360 nm wavelengths. Ca2+ imaging was as above, but Fluo4 was excited at 488 nm wavelength and emitted light above 510 nm collected as above.

Western blot analysis

Cell lysates from 20-50 mouse eggs were prepared by adding 2X-Laemmli sample buffer. Proteins were separated on 5% SDS-PAGE gels and transferred to PVDF membranes (Millipore, Bedford, MA). After blocking with 5% fat-free milk + TBS, membranes were probed with the rabbit polyclonal antibody specific to IP3R1 (1:1000; a generous gift from Dr. Jan Parys, Katholieke Universiteit, Leuven, Belgium; Parys et al., 1995). Goat anti-rabbit antibody conjugated to horseradish peroxidase (HRP) was used as a secondary antibody (1:5000; Goat anti-Rabbit IgG (H+L) Cross-Adsorbed Secondary Antibody, HRP; Invitrogen, Waltham, Ma). For detection of chemiluminescence, membranes were developed using ECL Prime (Sigma) and exposed for 1–3 min to maximum sensitivity film (VWR, Radnor, PA). Broad-range pre-stained SDS–PAGE molecular weight markers (Bio-Rad, Hercules, CA) were run in parallel to estimate the molecular weight of the immunoreactive bands. The same membranes were stripped at 50°C for 30 min (62.5 mM Tris, 2% SDS, and 100 mM 2-beta mercaptoethanol) and re-probed with anti-α-tubulin monoclonal antibody (1:1000).

Immunostaining and confocal microscopy

Immunostaining was performed according to our previous study (Akizawa et al., 2021). After incubation with or without TPEN, MII eggs were fixed with 4% (w/v) paraformaldehyde in house-made phosphate-buffered saline (PBS) for 20 min at room temperature and then permeabilized for 60 min with 0.2% (v/v) Triton X-100 in PBS. Next, the eggs were blocked for 45 min with a blocking buffer containing 0.2% (w/v) skim milk, 2% (v/v) fetal bovine serum, 1% (w/v) bovine serum albumin, 0.1% (v/v) TritonX-100, 0.75% (w/v) glycine in PBS. Eggs were incubated overnight at 4°C with mouse anti-HA antibody (1:200) diluted in blocking buffer. Eggs were washed in blocking buffer 3X for 10 min, followed by incubation at room temperature for 30 min with a secondary antibody, Alexa Fluor 488 goat anti-mouse IgG (H + L) (1:400) diluted in blocking buffer. Fluorescence signals were visualized using a laser-scanning confocal microscope (Nikon A1 Resonant Confocal with six-color TIRF) fitted with a 63×, 1.4 NA oil-immersion objective lens.

Statistical analysis

Comparisons for statistical significance of experimental values between treatments and experiments were performed in three or more experiments performed on different batches of eggs in most studies. Given the number of eggs needed, WB studies were repeated twice. Prism-GraphPad software was used to perform the statistical comparisons that include unpaired Student’s t-tests, Fisher’s exact test, and One-way ANOVA followed by Tukey’s multiple comparisons, as applicable, and the production of graphs to display the data. All data are presented as mean±s.d. Differences were considered significant at P < 0.05.